### 2023-01-11 submission.Rmd
lsa

---
title: Predicting Netflix Scores on Google 
author: Thalya Lim
# https://renkun.me/2022/03/06/my-recommendations-of-vs-code-extensions-for-r/
---

```{r}
x <- 1
y <- 2
```

### 2023-01-11 4_MachineLearning.r

@@ -8,11 +8,14 @@ library(lubridate)
 
 # Feature engineering - categories actors based on how popular they are 
 main <- read.csv(file = 'datasets/view_main_features.csv')
+main <- read.csv(file = 'datasets/view_main_lsa.csv')
+
 
 main$date_added <- as.Date(as.character(main$date_added))
+main$max.factor<-as.character(main$max.factor)
 
 
-main = subset(main, select = -c(plot,google_plot,id,title,scoreClass,duration_units))
+main = subset(main, select = -c(plot,google_plot,id,title,duration_units,item,max.value))
 
 row.number <- sample(1:nrow(main), 0.5*nrow(main))
 train = main[row.number,]

### 2023-01-11 Packages.r

@@ -2,3 +2,7 @@
 install.packages("RSQLite")
 install.packages("data.table")
 install.packages("lubridate")
+install.packages("quanteda.textmodels")
+install.packages("tm")
+install.packages("lsa")
+install.packages("ggplot2")

### 2023-01-12 Packages.r
save work

@@ -1,8 +1,11 @@
-# This script is for installing all the packages
-install.packages("RSQLite")
-install.packages("data.table")
-install.packages("lubridate")
-install.packages("quanteda.textmodels")
-install.packages("tm")
-install.packages("lsa")
-install.packages("ggplot2")
+# # This script is for installing all the packages
+# install.packages("RSQLite")
+# install.packages("data.table")
+# install.packages("lubridate")
+# install.packages("quanteda.textmodels")
+# install.packages("tm")
+# install.packages("lsa")
+# install.packages("ggplot2")
+# install.packages("knitr")
+install.packages("kableExtra")
+install.packages("reticulate")

### 2023-01-12 submission.Rmd
save work

@@
 ---
-title: Predicting Netflix Scores on Google 
+title: Can we predict the popularity of Netflix Shows? 
 author: Thalya Lim
+Logo: <Put picture of Netflix logo>
+output: 
+    rmarkdown::html_document:
+        theme: lumen
+        highlight: rstudio
 # https://renkun.me/2022/03/06/my-recommendations-of-vs-code-extensions-for-r/
+# https://haozhu233.github.io/kableExtra/awesome_table_in_html.html
 ---
+
+# About
+This project is about analysing what makes a show on Netflix more likeable?
+
+Are TV shows more well received than Movies?
+
+Are action movies more popular than rom-coms?
+
+Are shows from Korean more popular than Thai shows?
+
+This project aims to answer such questions
+
+# Data
+* Main dataset is Netflix Dataset from Kaggle 
+    + 8808 different titles, mix of TV series and movies, I will refer to both as shows
+    + shows added from 2014-2021
+    + shows released from 1925 up to 2021
+
+```{r}
+library(knitr)
+library(kableExtra)
+netflixData <- read.csv(file = 'datasets/dataset_main.csv')
+temp = head(netflixData, 10)
+temp %>%
+  kbl() %>%
+  kable_styling() %>%
+  column_spec(1, width = "10cm") %>%
+  scroll_box(width = "1000px", height = "500px")
+```
+
+* Review Scores and Supplementary info for each title scrapped from Google
++ To find the popularity of the show, the most important feature, we use the review how many people from Google likes it 
+< Put picture of squid game with the review in google search >
+
+```{r}
+library(reticulate)
+use_python("C:/venv/Scripts/python.exe")
+use_virtualenv("C:/venv")
+```
+
+```{python}
+import pandas as pd
+import requests
+import urllib
+from requests_html import HTML
+from requests_html import HTMLSession
+import bs4
+
+def get_source(url):
+    """Return the source code for the provided URL. 
+    Args: 
+        url (string): URL of the page to scrape.
+    Returns:
+        response (object): HTTP response object from requests_html. 
+    """
+
+    try:
+        session = HTMLSession()
+        response = session.get(url)
+        return response
+
+    except requests.exceptions.RequestException as e:
+        print(e)
+
+def get_googleInfo(title):
+
+    scrapedData = []
+
+    query = urllib.parse.quote_plus(title)
+    response = get_source("https://www.google.co.uk/search?q=" + query)
+
+    soup = bs4.BeautifulSoup(response.text,"html.parser")
+
+    rating_object=soup.find_all( "div", {"class":"a19vA"} )
+    info_object=soup.find_all( "div", {"class":"rVusze"} )
+    desc_object=soup.find_all( "div", {"class":"PZPZlf hb8SAc"} )
+
+    scrapedData.append('Title: ' +title)
+
+    for rating in rating_object:
+        ratingInfo = rating.getText()
+        rating = ratingInfo[0:3]
+        scrapedData.append('Rating: ' +rating)
+
+    for info in info_object:
+        info = info.getText()
+        if 'Language' in info:
+            scrapedData.append(info)
+            break
+
+    for info in info_object:
+        info = info.getText()
+        if 'Genre' in info:
+            scrapedData.append(info)
+            break
+
+    for desc in desc_object:
+        description = desc.getText()
+        description = description[0:11] + str(': ') + description[11:]
+        scrapedData.append(description)
+        break
+
+    return scrapedData
+
+# Test Function
+info = get_googleInfo("Squid Game")
+print(info)
+```
+
+Data Blending (header)
+We blend the Main Kaggle dataset with the Google dataset
+Using SQLite to join them, this gives us more versatility. Could've use the R joins but I feel most comfortable using SQL 
+Some shows could not be google so we use a left join on the main dataset 
+< show code from Data Cleaning.r >
+
+Data Cleaning (header)
+Renaming Features (sub-header)
++ id 
++ type
++ title
++ director
++ cast
++ country
++ date_added
++ release_year
++ rating
++ duration
++ genre
++ plot
++ score
++ google_language
++ google_genre
++ google_plot
+< code >
+
+Cleaning each feature (sub header) 
+Look for inconsistencies, duplicates, outliers, etc. 
+Changing type and formats
+Recatagorize 
++ id - check completeness
++ type - summary 
++ title - check completeness
++ director - summary
++ cast - summary 
++ country - summary
++ date_added - 
++ release_year
++ rating
++ duration
++ genre
++ plot
++ score
++ google_language
++ google_genre
++ google_plot
+
+Handle missing data (sub header)
+Missing reviews (sub sub header)
+Remove rows with no data on reviews
+< code >
+
+Analysing missing datapoints (sub sub header)
+< code >
+Pretty useless to have these features
+But I transform the fields into present/absent
+Just in case it has predictive capabilities
+< code >
 

### 2023-01-12 python files/PythonDataScraping.py

@@ -2,73 +2,71 @@
 import pandas as pd
 import requests
 import urllib
-import pandas as pd
 from requests_html import HTML
 from requests_html import HTMLSession
-import requests
 import bs4
 
-# # Defining Functions
-# def get_source(url):
-#     """Return the source code for the provided URL. 
+# Defining Functions
+def get_source(url):
+    """Return the source code for the provided URL. 
+    Args: 
+        url (string): URL of the page to scrape.
+    Returns:
+        response (object): HTTP response object from requests_html. 
+    """
 
-#     Args: 
-#         url (string): URL of the page to scrape.
+    try:
+        session = HTMLSession()
+        response = session.get(url)
+        return response
 
-#     Returns:
-#         response (object): HTTP response object from requests_html. 
-#     """
+    except requests.exceptions.RequestException as e:
+        print(e)
 
-#     try:
-#         session = HTMLSession()
-#         response = session.get(url)
-#         return response
+def get_googleInfo(title):
 
-#     except requests.exceptions.RequestException as e:
-#         print(e)
+    scrapedData = []
 
-# def get_googleInfo(title):
+    query = urllib.parse.quote_plus(title)
+    response = get_source("https://www.google.co.uk/search?q=" + query)
 
-#     scrapedData = []
-
-#     query = urllib.parse.quote_plus(title)
-#     response = get_source("https://www.google.co.uk/search?q=" + query)
-
-#     soup = bs4.BeautifulSoup(response.text,"html.parser")
+    soup = bs4.BeautifulSoup(response.text,"html.parser")
                         
-#     rating_object=soup.find_all( "div", {"class":"a19vA"} )
-#     info_object=soup.find_all( "div", {"class":"rVusze"} )
-#     desc_object=soup.find_all( "div", {"class":"PZPZlf hb8SAc"} )
+    rating_object=soup.find_all( "div", {"class":"a19vA"} )
+    info_object=soup.find_all( "div", {"class":"rVusze"} )
+    desc_object=soup.find_all( "div", {"class":"PZPZlf hb8SAc"} )
 
-#     scrapedData.append('Title: ' +title)
+    scrapedData.append('Title: ' +title)
 
-#     for rating in rating_object:
-#         ratingInfo = rating.getText()
-#         rating = ratingInfo[0:3]
-#         scrapedData.append('Rating: ' +rating)
+    for rating in rating_object:
+        ratingInfo = rating.getText()
[…]

### 2023-01-14 submission.Rmd
save work

--- 2023-01-11 submission.Rmd
@@
 ---
-title: Predicting Netflix Scores on Google 
+title: Can we explain the popularity of Netflix Shows? 
 author: Thalya Lim
+Logo: <Put picture of Netflix logo>
+output: 
+    rmarkdown::html_document:
+        theme: lumen
+        highlight: rstudio
 # https://renkun.me/2022/03/06/my-recommendations-of-vs-code-extensions-for-r/
+# https://haozhu233.github.io/kableExtra/awesome_table_in_html.html
 ---
 
+# About
+This project is about analysing what makes a show on Netflix more likeable?
+
+Are TV shows more well received than Movies?
+
+Are action movies more popular than rom-coms?
+
+Are shows from Korean more popular than Thai shows?
+
+This project aims to answer such questions via going through the whole process of creating a machine learning model
+
+# Packages
+Before we get started. We will load all the relevant Pacakages
+```{r load packages, message=FALSE}
+library(reticulate)
+library(DBI)
+library(dplyr)
+library(lubridate)
+library(tidyr)
+library(data.table)
+library(quanteda)
+library(tm)
+library(lsa)
+library("quanteda.textmodels")
+library(ggplot2)
+library(kableExtra)
+```
+
+I also use a bit of Python for this project, so I will load some Python packages too
+
+```{r echo=FALSE,}
+use_python("C:/venv/Scripts/python.exe")
+use_virtualenv("C:/venv")
+```
+
+```{python}
+import pandas as pd
+import requests
+import urllib
+from requests_html import HTML
+from requests_html import HTMLSession
+import bs4
+```
+
+# Getting Data
+
+I use two main data sources for this project, namely Kaggle and Google Search Results
+
+### Source 1: Kaggle 
+This dataset provides us with a list of Netflix Shows along with information such as the year it was added, duration, cast, description etc..
+There are altogether 8808 Netflix Shows in this dataset.
 ```{r}
-x <- 1
-y <- 2
+netflixData <- read.csv(file = 'datasets/dataset_main.csv')
 ```
+```{r echo=FALSE}
+# FOR Displaying results
+# temp = head(netflixData, 10)
+# temp %>%
+#   kbl() %>%
+#   kable_styling() %>%
+#   column_spec(1, width = "10cm") %>%
+#   scroll_box(width = "1000px", height = "500px")
+```
+
+### Source 2: Google Search Results 
+To represent popularity, I will use Google Review Scores, this is also going to be my dependent variable. 
+In order to supplement the information from the Kaggle dataset, I extracted other information from Google which will hopefully also serve as independent features.
+
+The image below shows an example of the data that will be collected for each of the 8808 shows in the Kaggle Dataset, namely Review Score, Description, Genre and Language
+
+```{r pressure, echo=FALSE, out.width = '100%'}
+knitr::include_graphics("Search Example.JPG")
+```
+
+#### Google Scrapping Method
+```{python}
+def get_source(url):
+    try:
+        session = HTMLSession()
+        response = session.get(url)
+        return response
+    except requests.exceptions.RequestException as e:
+        print(e)
+
+def get_googleInfo(title):
+    scrapedData = []
+
+    query = urllib.parse.quote_plus(title)
+    response = get_source("https://www.google.co.uk/search?q=" + query)
+    soup = bs4.BeautifulSoup(response.text,"html.parser")
+
+    rating_object=soup.find_all( "div", {"class":"a19vA"} )
+    info_object=soup.find_all( "div", {"class":"rVusze"} )
+    desc_object=soup.find_all( "div", {"class":"PZPZlf hb8SAc"} )
+
+    scrapedData.append('Title: ' +title)
+
+    for rating in rating_object:
+        ratingInfo = rating.getText()
+        rating = ratingInfo[0:3]
+        scrapedData.append('Rating: ' +rating)
+
+    for info in info_object:
+        info = info.getText()
+        if 'Language' in info:
+            scrapedData.append(info)
+            break
+
+    for info in info_object:
+        info = info.getText()
+        if 'Genre' in info:
+            scrapedData.append(info)
+            break
+
+    for desc in desc_object:
+        description = desc.getText()
+        description = description[0:11] + str(': ') + description[11:]
+        scrapedData.append(description)
+        break
+
+    return scrapedData
+```
+Here is an example of Output, when we insert the hit show "Squid Game" into the method above.
+
+``` {python}
+info = get_googleInfo("Squid Game")
+print(info)
+```
+
+Load Google Search Results dataset.
+``` {r}
+googleData <- read.csv(file = 'datasets/dataset_googleScraped.csv')
+```
+
+### Joining the Kaggle Dataset and Google Search Results
+I combine both datasets. 
+```{r}
+con <- dbConnect(RSQLite::SQLite(), ":memory:")
+
+dbWriteTable(con, "netflixData", netflixData)
+dbWriteTable(con, "googleData", googleData)
+
+query <- "SELECT netflixData.show_id
+        , netflixData.type
+        , netflixData.title
+        , netflixData.director
+        , netflixData.cast
+        , netflixData.country
+        , netflixData.date_added
+        , netflixData.release_year
+        , netflixData.rating
+        , netflixData.duration
+        , netflixData.listed_in
+        , netflixData.description
+        , googleData.Likes
+        , googleData.Languages
+        , googleData.Genres
+        , googleData.Descriptions
+        FROM netflixData left join googleData 
+        ON netflixData.show_id= googleData.show_id"
+res <- dbSendQuery(con, query)
+df <- dbFetch(res)
+
+dbClearResult(res)
+```
+
+# Data Transformation
+## Renaming Columns
+I rename the columns because some of them had the same names. 
+Independent features that were scraped from Google have "google_" at the front of them.
+``` {r}
+new_names <- c("id" 
+        , "type"
+        , "title"
+        , "director"
+        , "cast"
+        , "country"
+        , "date_added"
+        , "release_year"
+        , "rating"
+        , "duration"
+        , "genre"
+        , "plot"
+        , "google_score"
+        , "google_language"
+        , "google_genre"
+        , "google_plot")
+df <- setNames(df, new_names)
+```
+## Data Preview
+Here is what the dataset looks like now, we can see all the features that will be used:
+``` {r echo=FALSE}
+temp = head(df, 10)
+temp %>%
+  kbl() %>%
+  kable_styling() %>%
+  column_spec(1, width = "10cm") %>%
+  scroll_box(width = "1000px", height = "500px")
+```
+
+## Drop rows
+As expected, the Google search results of some Netflix Shows did not give us a Google Review Score.
+I drop these rows because there is no point keeping rows with no Dependent Feature.
+
+```{r}
+df <- df[grep("%", df$google_score),]
+```
+
+# Data Exploration
+
+### Missing Data
+```{r}
+count_blanks <- function(feature) {
+    string1 <- feature
+    string2 <- '== ""'
+    subset = paste(string1, string2)
+    subset <- subset(df, eval(parse(text=subset)))
+    count <- count(subset)
+  return(count)
+}
+
+feature <- new_names # retrieving all the column names
+
+NA_Count <- c(
+ toString(count_blanks('id'))
+, toString(count_blanks('type'))
+, toString(count_blanks('title'))
+, toString(count_blanks('director'))
+, toString(count_blanks('cast'))
+, toString(count_blanks('country'))
+, toString(count_blanks('date_added'))
+, toString(count_blanks('release_year'))
+, toString(count_blanks('rating'))
+, toString(count_blanks('duration'))
+, toString(count_blanks('genre'))
+, toString(count_blanks('plot'))
+, toString(count_blanks('google_score'))
+, toString(count_blanks('google_language'))
+, toString(count_blanks('google_genre'))
+, toString(count_blanks('google_plot')))
+NA_Count <- data.frame(feature, NA_Count)
+
+print(NA_Count)
+
+```
+
+# Cleaning each feature (sub header) 
+Look for inconsistencies, duplicates, outliers, etc. 
+Changing type and formats
+Recatagorize 
++ id - check completeness
++ type - summary 
++ title - check completeness
++ director - summary
++ cast - summary 
++ country - summary
++ date_added - 
++ release_year
++ rating
++ duration
++ genre
++ plot
++ google_score
++ google_language
++ google_genre
++ google_plot
+
+Handle missing data (sub header)
+Missing reviews (sub sub header)
+Remove rows with no data on reviews
+< code >
+
+Analysing missing datapoints (sub sub header)
+< code >
+Pretty useless to have these features
+But I transform the fields into present/absent
+Just in case it has predictive capabilities
+< code > 
+# See if type needs cleaning
+
+``` {r}
+view <- df %>% group_by(type) %>% summarise(count = n()) # Show types and count by each type
+print(view)
+```
+
+director
+``` {r}
+view <- df %>% group_by(director) %>% summarise(count = n()) # Show directors and count by each director group
+print(view)
+```
+Some of the rows have more than one director (will make maping tables)
+
+# See if country needs cleaning
+``` {r}
+view <- df %>% group_by(country) %>% summarise(count = n()) # Show country and count by each country group
+
+```
+# Many of the rows have more than one country (will make maping tables)
+
+# See if date_added needs cleaning
+``` {r}
+view <- df %>% group_by(date_added) %>% summarise(count = n()) # Show date_added and count by each date_added
+```
+# Change to date format
+``` {r}
+df$date_added <- mdy(df$date_added)
+```
+# See if release year needs cleaning
+``` {r}
+view <- df %>% group_by(release_year) %>% summarise(count = n()) # Show release_year and count by each release_year
+```
+# See if rating needs cleaning
+``` {r}
+
+view <- df %>% group_by(rating) %>% summarise(count = n()) # Show release_year and count by each release_year
+df$rating[df$rating == "PG-13" ] <- "PG"
+df$rating[df$rating == "TV-PG" ] <- "PG"
+df$rating[df$rating == "TV-14" ] <- "PG"
+df$rating[df$rating == "TV-G" ] <- "G"
+df$rating[df$rating == "TV-MA" ] <- "R"
+df$rating[df$rating == "TV-Y7" ] <- "Y"
+df$rating[df$rating == "TV-Y7-FV" ] <- "Y"
+df$rating[df$rating == "TV-Y" ] <- "Y"
+df$rating[df$rating == "NR" ] <- "UR"
+
+```
+# See if duration needs cleaning
+``` {r}
+view <- df %>% group_by(duration) %>% summarise(count = n()) # Show duration and count by each release_year
+```
+# Duration convert blanks to NA
+# Convert duration to numeric
+
+``` {r}
+df$duration[df$duration ==""] <- NA
+df <- separate(df, duration, c("duration", "duration_units"))
+df <- transform(df, duration = as.numeric(duration))
+```
+
+# See if genre needs cleaning
+``` {r}
+view <- df %>% group_by(genre) %>% summarise(count = n()) # Show genre and count by each genre
+```
+
+# See if plot needs cleaning
+``` {r}
+view <- df %>% group_by(plot) %>% summarise(count = n()) # Show plot and count by each plot
+```
+
+# See if google_score needs cleaning
+``` {r}
+view <- df %>% group_by(google_score) %>% summarise(count = n()) # Show google_score and count by each google_score
+```
+
+# Remove % and convert to numeric type
+``` {r}
+df$google_score<-gsub("%","",as.character(df$google_score))
+df <- transform(df, google_score = as.numeric(google_score))
+```
+
+Transform google_language and google_genre feature into present/absent because it was not scrappable
+``` {r}
+df$google_language <- ifelse(df$google_language =="", "absent", "present")
+view <- df %>% group_by(google_language) %>% summarise(count = n())  # Show categories and count by each category
+print(view)
+```
+``` {r}
+df$google_genre <- ifelse(df$google_genre =="", "absent", "present")
+view <- df %>% group_by(google_genre) %>% summarise(count = n())
+print(view)
+```
+
+``` {r}
+write.csv(df, "datasets/view_main_cleaned.csv", row.names=FALSE)
+df <- read.csv(file = 'datasets/view_main_cleaned.csv')
+```
+
+# Mapping Tables 
+# Build Country Mapping Table
+``` {r}
+
+country_mapping <- df %>%
+    mutate(country = strsplit(as.character(country), ",")) %>%
+    unnest(country)
+
+country_mapping = subset(country_mapping, select = c(id, country))
+country_mapping$country <- trimws(country_mapping$country, which = c("left"))
+
+write.csv(country_mapping, "datasets/mapping_country.csv", row.names=FALSE)
+```
+
+# # Build Director Mapping Table
+``` {r}
+
+director_mapping <- df %>%
+    mutate(director = strsplit(as.character(director), ",")) %>%
+    unnest(director)
+
+director_mapping = subset(director_mapping, select = c(id, director))
+director_mapping$director <- trimws(director_mapping$director , which = c("left"))
+write.csv(director_mapping, "datasets/mapping_director.csv", row.names=FALSE)
+```
+
+# # Build Cast Mapping Table
+``` {r}
+cast_mapping <- df %>%
+    mutate(cast = strsplit(as.character(cast), ",")) %>%
+    unnest(cast)
+
+cast_mapping = subset(cast_mapping, select = c(id, cast))
+cast_mapping$cast <- trimws(cast_mapping$cast, which = c("left"))
+write.csv(cast_mapping, "datasets/mapping_cast.csv", row.names=FALSE)
+```
+
+# # Build Genre Mapping Table
+``` {r}
+genre_mapping <- df %>%
+    mutate(genre = strsplit(as.character(genre), ",")) %>%
+    unnest(genre)
+
+genre_mapping = subset(genre_mapping, select = c(id, genre))
+genre_mapping$cast <- trimws(genre_mapping$genre, which = c("left"))
+write.csv(genre_mapping, "datasets/mapping_genre.csv", row.names=FALSE)
+```
+
+# Trim dataset for better performance
+``` {r}
+df = subset(df, select = -c(country,director,cast,genre) )
+```
+
+#Get top 100 actors and actress from IMDB list
+
+# Feature engineering - categories actors based on how popular they are 
+``` {r}
+popularActors <- read.csv(file = 'datasets/dataset_popular_actors.csv')
+
+# Create new column and set default value to "top 1000"
+popularActors$rank_category <- "top 1000"
+setDT(popularActors)
+
+popularActors$rank_category[popularActors$Position < 501 ] <- "top 500"
+popularActors$rank_category[popularActors$Position < 201 ] <- "top 200"
+popularActors$rank_category[popularActors$Position < 101 ] <- "top 100"
+popularActors$rank_category[popularActors$Position < 51 ] <- "top 50"
+popularActors$rank_category[popularActors$Position < 21 ] <- "top 20"
+popularActors$rank_category[popularActors$Position < 11 ] <- "top 10"
+
+popularActors <- separate(popularActors, Description, c("Points", "Description"))
+popularActors <- transform(popularActors, Points = as.numeric(Points))
+
+# View(popularActors)
+
+write.csv(popularActors, "datasets/view_popular_actors.csv", row.names=FALSE)
+```
+
+# Feature engineering - categories actors based on how popular they are 
+``` {r}
+popularActresses <- read.csv(file = 'datasets/dataset_popular_actresses.csv')
+
+# Create new column and set default value to "top 1000"
+popularActresses$rank_category <- "top 1000"
+setDT(popularActresses)
+
+popularActresses$rank_category[popularActresses$Position < 501 ] <- "top 500"
+popularActresses$rank_category[popularActresses$Position < 201 ] <- "top 200"
+popularActresses$rank_category[popularActresses$Position < 101 ] <- "top 100"
+popularActresses$rank_category[popularActresses$Position < 51 ] <- "top 50"
+popularActresses$rank_category[popularActresses$Position < 21 ] <- "top 20"
+popularActresses$rank_category[popularActresses$Position < 11 ] <- "top 10"
+
+# Get points from actresses
+popularActresses <- separate(popularActresses, Description, c("Points", "Description"))
+popularActresses <- transform(popularActresses, Points = as.numeric(Points))
+
+# View(popularActresses)
+
+write.csv(popularActresses, "datasets/view_popular_actresses.csv", row.names=FALSE)
+```
+
+# Feature engineering - categories directors based on how popular they are 
+``` {r}
+popularDirectors <- read.csv(file = 'datasets/dataset_popular_directors.csv')
+
+# Create new column and set default value to "top 1000"
+popularDirectors$rank_category <- "top 1000"
+setDT(popularDirectors)
+
+popularDirectors$rank_category[popularDirectors$Position < 501 ] <- "top 500"
+popularDirectors$rank_category[popularDirectors$Position < 201 ] <- "top 200"
+popularDirectors$rank_category[popularDirectors$Position < 101 ] <- "top 100"
+popularDirectors$rank_category[popularDirectors$Position < 51 ] <- "top 50"
+popularDirectors$rank_category[popularDirectors$Position < 21 ] <- "top 20"
+popularDirectors$rank_category[popularDirectors$Position < 11 ] <- "top 10"
+
+#Get points from directors
+popularDirectors <- separate(popularDirectors, Description, c("Points", "Description"))
+popularDirectors <- transform(popularDirectors, Points = as.numeric(Points))
+
+# View(popularDirectors)
+
+write.csv(popularDirectors, "datasets/view_popular_directors.csv", row.names=FALSE)
+```
+
+# Create an ephemeral in-memory RSQLite database
+#``` {r}
+
+con <- dbConnect(RSQLite::SQLite(), ":memory:")
+
+main <- read.csv(file = 'datasets/view_main_trimmed.csv')
+cast <- read.csv(file = 'datasets/mapping_cast.csv')
+actorsPoints <- read.csv(file = 'datasets/view_popular_actors.csv')
+actressesPoints <- read.csv(file = 'datasets/view_popular_actresses.csv')
+directors <- read.csv(file = 'datasets/mapping_director.csv')
+directorsPoints <- read.csv(file = 'datasets/view_popular_directors.csv')
+
+dbWriteTable(con, "main", main)
+dbWriteTable(con, "cast", cast)
+dbWriteTable(con, "actorsPoints", actorsPoints)
+dbWriteTable(con, "actressesPoints", actressesPoints)
+dbWriteTable(con, "directors", directors)
+dbWriteTable(con, "directorsPoints", directorsPoints)
+
+# Attach the points to the mapping table
+query <- "SELECT c.id
+                ,c.cast
+                ,CASE WHEN a.Points IS NOT NULL THEN a.Points
+                WHEN b.Points IS NOT NULL THEN b.Points 
+                ELSE 0 END AS Points
+                FROM cast c
+                LEFT JOIN actorsPoints a ON c.cast = a.Name
+                LEFT JOIN actressesPoints b ON c.cast = b.Name"
+res <- dbSendQuery(con, query)
+castPointsMapping <- dbFetch(res)
+dbClearResult(res)
+
+dbWriteTable(con, "castPointsMapping", castPointsMapping)
+
+#Attach the director to the mapping table
+query <- "SELECT a.id
+                ,a.director
+                ,CASE WHEN d.Points IS NOT NULL THEN d.Points
+                ELSE 0 END AS Points
+                FROM directors a
+                LEFT JOIN directorsPoints d ON a.director = d.Name"
+res <- dbSendQuery(con, query)
+directorPointsMapping <- dbFetch(res)
+dbClearResult(res)
+
+dbWriteTable(con, "directorPointsMapping", directorPointsMapping)
+
+query <- "SELECT a.*
+        , CASE WHEN c.Points IS NOT NULL THEN max(c.Points)
+        ELSE 0 END AS cast_points
+        , CASE WHEN d.Points IS NOT NULL THEN max(d.Points)
+        ELSE 0 END AS director_points
+        FROM main a 
+        LEFT JOIN castPointsMapping c ON a.id = c.id 
+        LEFT JOIN directorPointsMapping d ON a.id = d.id 
+        GROUP BY a.id"
+
+res <- dbSendQuery(con, query)
+df <- dbFetch(res)
+
+dbClearResult(res)
+#```
+
+# Seperate google_scores into bins
+#``` {r}
+# df$google_scoreClass <- cut(df$google_score, breaks=c(0,60,70,80,90,100), labels=c("0-60","61-70","71-80","81-90","90-100"))
+
+write.csv(df, "datasets/view_main_features.csv", row.names=FALSE)
+
+dbDisconnect(con)
+#```
+
+# Latent Semantic Analysis of Plot and google plot data
+``` {r}
+
+```
+# load data
+
+#``` {r}
+main <- read.csv(file = 'datasets/view_main_features.csv')
+main$plot_combined <- paste(main$plot,main$google_plot)
+#```
+# Convert data to corpus
+#``` {r}
+corpus <- Corpus(VectorSource(main$plot_combined))
+#```
+
+# Remove special characters, case, punctuation and numbers
+#``` {r}
+
+removeSpecialChars <- function(x) gsub("[^a-zA-Z0-9 ]","",x)
+corpus <- tm_map(corpus, removeSpecialChars)
+corpus <- tm_map(corpus, removeNumbers)
+corpus <- tm_map(corpus, removePunctuation)
+corpus <- tm_map(corpus, content_transformer(tolower))
+#```
+
+# Remove stop words
+#``` {r}
+corpus <- tm_map(corpus, removeWords, stopwords("english"))
+#```
+
+# Remove white space
+#``` {r}
+corpus <- tm_map(corpus, stripWhitespace)
+#```
+
+# Stemming
+#``` {r}
+corpus <- tm_map(corpus, stemDocument)
+#```
+
+# Term document matrix
+#``` {r}
+tdm <- TermDocumentMatrix(corpus)
+#```
+
+# View top 5 most frequently occuring term
+#``` {r}
+tdmMatrix <- as.matrix(tdm)
+v <- sort(rowSums(tdmMatrix), decreasing=TRUE)
+d <- data.frame(word=names(v),freq=v)
+print(head(d,5))
+#```
+
+# Weighting 
+#``` {r}
+tdm2 <- as.textmatrix(as.matrix(tdm))
+tdm.weighted <- lw_logtf(tdm2)
+print(tdm.weighted)
+#```
+
+# Latent Semantic Analysis
+#``` {r}
+lsa <- lsa(tdm.weighted, dims=10)
+
+Tk <- lsa$tk
+Sk <- lsa$sk
+Dk <- lsa$dk 
+#```
+
+# Varimax Rotation
+#``` {r}
+Tk.varimax <- varimax(Tk)
+
+Dk.rotated <- Dk %*% Tk.varimax$rotmat
+Tk.rotated <- Tk %*% Tk.varimax$rotmat 
+#```
+
+# Interreting Term and Document Matrices
+#``` {r}
+
+sort.loadings.table <- function(x) {
+    factor.names <- colnames(x)
+    x <- as.data.frame(x)
+    x$max.factor <- apply(abs(x),1,which.max)
+    x$max.value <- x[cbind(1:nrow(x),x$max.factor)]
+    x <- x[order(x$max.factor,-abs(x$max.value)),]
+    x$item <- rownames(x)
+    rownames(x) <- NULL
+    x
+}
+
+threshold.loadings.table <- function (x,q=0.1) {
+    threshold <- quantile(abs(x$max.value),probs=1-q)
+    x <- subset(x,abs(x$max.value)>threshold)
+    x
+}
+
+Tk.thresholded <- as.data.table(threshold.loadings.table(sort.loadings.table(Tk.rotated),q=0.02))
+write.csv(Tk.thresholded[,.(item, max.factor, max.value)], "datasets/tk.csv", row.names=FALSE)
+
+Dk.thresholded <- as.data.table(threshold.loadings.table(sort.loadings.table(Dk.rotated),q=1))
+# print(Dk.thresholded[,.(item,max.factor,max.value)])
+write.csv(Dk.thresholded[,.(item,max.factor,max.value)],"datasets/dk.csv", row.names=FALSE)
+#```
+#``` {r}
+biplot <- function(Tk,Dk,xdim,ydim,Tk.scale=1,...){
+    print("made it")
+    Tk[,type:="Terms"]
+    Dk[,type:="Title"]
+    biplot.data <- rbindlist(list(Tk,Dk))
+    setnames(biplot.data,xdim,"F1")
+    setnames(biplot.data,ydim,"F2")
+    biplot.data[type=="Terms",F1:=F1*Tk.scale]
+    biplot.data[type=="Terms",F2:=F2*Tk.scale]
+    ggplot(biplot.data, aes(x=F1, y=F2, label=item, col=type)) + geom_text()
+}
+
+plot(biplot(Tk=Tk.thresholded,Dk=Dk.thresholded, xdim="V1", ydim="V2", Tk.scale=2))
+#```
+
+# Join LSA data to main dataframe
+
+#``` {r}
+
+con <- dbConnect(RSQLite::SQLite(), ":memory:")
+
+main <- read.csv(file = 'datasets/view_main_features.csv')
+lsa <- read.csv(file = 'datasets/lsa_2.csv')
+
+lsa$item <- sub("^", "s", lsa$item )
+
+dbWriteTable(con, "main", main)
+dbWriteTable(con, "lsa", lsa)
+
+query <- "SELECT m.*, l.*
+                FROM main m
+                LEFT JOIN lsa l ON m.id = l.item"
+res <- dbSendQuery(con, query)
+df <- dbFetch(res)
+dbClearResult(res)
+setDT(df)
+View(df)
+
+write.csv(df, "datasets/view_main_lsa.csv", row.names=FALSE)
+
+dbDisconnect(con)
+#```
+
+# Machine learning model Multi Regressions
+#``` {r}
+main <- read.csv(file = 'datasets/view_main_lsa.csv')
+
+main$date_added <- as.Date(as.character(main$date_added))
+main$max.factor<-as.character(main$max.factor)
+
+main = subset(main, select = -c(plot,google_plot,id,title,duration_units,item,max.value))
+
+row.number <- sample(1:nrow(main), 0.5*nrow(main))
+train = main[row.number,]
+test = main[-row.number,]
+
+print("running regression.....")
+model1 = lm(log(google_score)~., data=train)
+print(summary(model1))
+#```

### 2023-01-21 submission.Rmd
save work

@@
 ---
+
+```{r echo=FALSE, out.width = '100%'}
+knitr::include_graphics("netflixHomepage.JPG")
+```
 
@@
 library(kableExtra)
+library(Hmisc)
 ```
@@
 This dataset provides us with a list of Netflix Shows along with information such as the year it was added, duration, cast, description etc..
-There are altogether 8808 Netflix Shows in this dataset.
+There are altogether 8807 Netflix Shows in this dataset.
 ```{r}
@@
 ### Source 2: Google Search Results 
-To represent popularity, I will use Google Review Scores, this is also going to be my dependent variable. 
-In order to supplement the information from the Kaggle dataset, I extracted other information from Google which will hopefully also serve as independent features.
+The Kaggle dataset doesn’t contain any feature that gives us information about how popular or likable a show was. 
+However, with the Netflix Show title, we can perform some web scraping to obtain Review Scores and other information off Google.
 
 The image below shows an example of the data that will be collected for each of the 8808 shows in the Kaggle Dataset, namely Review Score, Description, Genre and Language
-
-```{r pressure, echo=FALSE, out.width = '100%'}
+To represent popularity, I will use Google Review Scores, this is also going to be my dependent variable. 
+```{r echo=FALSE, out.width = '100%'}
 knitr::include_graphics("Search Example.JPG")
@@
 
-#### Google Scrapping Method
+Google Scrapping Method
+Below is the method I use to scrap data off Google. 
 ```{python}
@@
 
-Load Google Search Results dataset.
+Apply data scraping function on all movie/show titles in dataset. 
+Once all the information has been scraped, I write it into a csv file (full code in GitHub).
+``` {python eval = FALSE}
+# data = pd.read_csv('netflix_titles.csv')
+# goolgeInfo = data['title'].apply(get_googleInfo)
+# goolgeInfo.to_csv('googleInfo.csv', encoding='utf-8', index=False)
+print("hi")
+```
+
+Since the data scrapping was done in Python, I now need to load all Google Search Results data into the R world of this project.
 ``` {r}
@@
 
-# Data Transformation
+Both datasets are now joined but the feature names are quite confusing still. I will rename the features before showing a preview of the full combined dataset I will be working with.
+
+# Previewing Raw Data
 ## Renaming Columns
@@
 
-## Drop rows
-As expected, the Google search results of some Netflix Shows did not give us a Google Review Score.
-I drop these rows because there is no point keeping rows with no Dependent Feature.
+# Cleaning the data
 
-```{r}
-df <- df[grep("%", df$google_score),]
+## Removing duplicates or irrelevant observations
+## Dealing with duplicates 
+Checking if there are any duplicated Netflix Shows
+``` {r}
+print(length(unique(df$title)))
 ```
 
-# Data Exploration
+``` {r}
+print(df[duplicated(df$title),])
+```
+The Netflix shows that were thought to be duplicates by the code before seemed like dates instead.
+No duplicates. So we can move on.
 
-### Missing Data
-```{r}
+### Drop rows
+Any Netflix Show which does not have a Google Review Score (crucial dependent variable) is an irrelevant observation since it cannot be used for Analysis.
+``` {r}
 count_blanks <- function(feature) {
@@
 
-feature <- new_names # retrieving all the column names
+print(count_blanks('google_score'))
+```
 
-NA_Count <- c(
- toString(count_blanks('id'))
-, toString(count_blanks('type'))
-, toString(count_blanks('title'))
-, toString(count_blanks('director'))
-, toString(count_blanks('cast'))
-, toString(count_blanks('country'))
-, toString(count_blanks('date_added'))
-, toString(count_blanks('release_year'))
-, toString(count_blanks('rating'))
-, toString(count_blanks('duration'))
-, toString(count_blanks('genre'))
-, toString(count_blanks('plot'))
-, toString(count_blanks('google_score'))
-, toString(count_blanks('google_language'))
-, toString(count_blanks('google_genre'))
-, toString(count_blanks('google_plot')))
-NA_Count <- data.frame(feature, NA_Count)
+As expected, the Google search results of some Netflix Shows did not give us a Google Review Score. I drop these rows.
+```{r}
+df <- df[grep("%", df$google_score),]
+```
+Below shows and example of a Show which does not give us a Google Review Score
+```{r echo=FALSE, out.width = '100%'}
+knitr::include_graphics("NoGoogleScore.JPG")
+```
 
-print(NA_Count)
+We are now left with 6511 rows.
+``` {r}
+print(length(unique(df$title)))
+```
+
+## Fixing structural errors.
+Structural errors are when you measure or transfer data and notice strange naming conventions, typos, or incorrect capitalization.
+These inconsistencies can cause mislabeled categories or classes.
+For example, you may find “N/A” and “Not Applicable” both appear, but they should be analyzed as the same category.
+Changing data types
+
+We will look feature by feature for structural errors.
+
+1. Type
+``` {r}
+view <- df %>% group_by(type) %>% summarise(count = n())
+print(view)
+```
+The type feature looks clean, no action will be taken on it.
+Action: None
+
+2. director
+``` {r}
+view <- df %>% group_by(director) %>% summarise(count = n())
+print(view)
+```
+Some of the rows have more than one director. 
+Action: In the next Feature Engineering Section, I will make mapping tables and use feature engineering to capture this variable
+
+3. Cast
+``` {r}
+view <- df %>% group_by(cast) %>% summarise(count = n())
+print(view)
+```
+As expected, many Shows have more than one cast member. 
+Action: Similar to what will be done with the Director Feature, I will make mapping tables and use feature engineering to capture this variable
+
+3. Country
+``` {r}
+view <- df %>% group_by(country) %>% summarise(count = n())
+print(view)
+```
+Some shows originated from several different countries.
+Action: Similar to what will be done with the Director and Cast Feature, I will make mapping tables and use feature engineering to capture this variable.
+
+4. Date Added
+``` {r}
+view <- df %>% group_by(date_added) %>% summarise(count = n())
+print(view)
+print(typeof(df$date_added))
+```
+Date Added is in the character format.
+Action: Change this to date format
+``` {r}
+df$date_added <- mdy(df$date_added)
+```
+
+5. Release Year
+``` {r}
+view <- df %>% group_by(release_year) %>% summarise(count = n()) # Show release_year and count by each release_year
+print(view)
+print(typeof(df$release_year))
+```
+Release Year has the integer type. No noticable structural error.
+Action: None
+
+6. Rating
+``` {r}
+view <- df %>% group_by(rating) %>% summarise(count = n()) # Show release_year and count by each release_year
+print(view)
+```
+There are several categories which have the same meaning.
+Action: Consolidate the categories
+
+Consolidate the categories of the Rating Feature
+```{r}
+df$rating[df$rating == "PG-13" ] <- "PG"
+df$rating[df$rating == "TV-PG" ] <- "PG"
+df$rating[df$rating == "TV-14" ] <- "PG"
+df$rating[df$rating == "TV-G" ] <- "G"
+df$rating[df$rating == "TV-MA" ] <- "R"
+df$rating[df$rating == "NC-17" ] <- "R"
+df$rating[df$rating == "TV-Y7" ] <- "Y"
+df$rating[df$rating == "TV-Y7-FV" ] <- "Y"
+df$rating[df$rating == "TV-Y" ] <- "Y"
+df$rating[df$rating == "NR" ] <- "UR"
+df$rating[df$rating == "66 min" ] <- "UR"
+df$rating[df$rating == "84 min" ] <- "UR"
+
+view <- df %>% group_by(rating) %>% summarise(count = n()) # Show release_year and count by each release_year
+print(view)
+```
+
+7. Duration
+``` {r}
+view <- df %>% group_by(duration) %>% summarise(count = n()) # Show duration and count by each release_year
+print(view)
+```
+Durations with two different units are in the same feature. Also, we can remove their units to make it integers.
+Action: Split column into two different types of durations, remove units
+``` {r}
+df$duration[df$duration ==""] <- NA
+df$duration_min <- ifelse(grepl("min", df$duration),df$duration,NA)
+df$duration_season <- ifelse(grepl("Season", df$duration),df$duration,NA)
+print(head(df, 10))
+```
+
+Remove string from duration and convert character to integer
+``` {r}
+df$duration_min <-  gsub('min','',df$duration_min)
+df$duration_min <- as.numeric(df$duration_min)
+df$duration_season <-  gsub('Seasons','',df$duration_season)
+df$duration_season <-  gsub('Season','',df$duration_season)
+df$duration_season <- as.numeric(df$duration_season)
+print(head(df,10))
+```
+
+Drop duration column
+```{r}
+df = subset(df, select = -c(duration))
+```
+
+8. Genre
+``` {r}
+view <- df %>% group_by(genre) %>% summarise(count = n()) # Show genre and count by each genre
+print(view)
+```
+Some of the rows have more than one genre. 
+Action: In the next Feature Engineering Section, I will make mapping tables and use feature engineering to capture this variable
+
+9. Plot
+Plot contains text data.
+Action: Use Latent Semantic Analysis to categorize plots
+
+10. Google Score
+``` {r}
+view <- df %>% group_by(google_score) %>% summarise(count = n()) # Show google_score and count by each google_score
+print(view)
+```
+Symbol exist and type is character
+Action: remove symbol and convert type to numeric
+
+11. Google Score
+``` {r}
+df$google_score<-gsub("%","",as.character(df$google_score))
+df <- transform(df, google_score = as.numeric(google_score))
+```
+
+12. Google Language
+``` {r}
+print(head(df$google_language), 10)
+```
+Clear that a lot of data is missing.
+Action: Extract feature from it (present/absent)
+
+Transform google_language and google_genre feature into present/absent because it was not scrappable
+view <- df %>% group_by(google_language) %>% summarise(count = n())  # Show categories and count by each category
+df$google_language <- ifelse(df$google_language =="", "absent", "present")
+print(view)
+df$google_genre <- ifelse(df$google_genre =="", "absent", "present")
+view <- df %>% group_by(google_genre) %>% summarise(count = n())
+print(view)
+
+13. Google Genre
+
+``` {r}
+print(head(df$google_language), 10)
+```
+Clear that a lot of data is missing.
+Action: Extract feature from it (present/absent)
+
+``` {r}
+#write.csv(df, "datasets/view_main_cleaned.csv", row.names=FALSE)
+#df <- read.csv(file = 'datasets/view_main_cleaned.csv')
+```
+
+## Handle Missing data
+
+### Missing Data
+``` {r}
+#desc <- describe(df)
+#print(desc)
+```
+
+```{r}
+#feature <- new_names # retrieving all the column names
+
+#NA_Count <- c(
+#  toString(count_blanks('id'))
+# , toString(count_blanks('type'))
+# , toString(count_blanks('title'))
+# , toString(count_blanks('director'))
+# , toString(count_blanks('cast'))
+# , toString(count_blanks('country'))
+# , toString(count_blanks('date_added'))
+# , toString(count_blanks('release_year'))
+# , toString(count_blanks('rating'))
+# , toString(count_blanks('duration'))
+# , toString(count_blanks('genre'))
+# , toString(count_blanks('plot'))
+# , toString(count_blanks('google_score'))
+# , toString(count_blanks('google_language'))
+# , toString(count_blanks('google_genre'))
+# , toString(count_blanks('google_plot')))
+#NA_Count <- data.frame(feature, NA_Count)
+
+#print(NA_Count)
 
 ```
+
+* Validate
+
+* Step 3: Filter unwanted outliers
 
@@
 < code >
-# See if type needs cleaning
-
-``` {r}
-view <- df %>% group_by(type) %>% summarise(count = n()) # Show types and count by each type
-print(view)
-```
-
-director
-``` {r}
-view <- df %>% group_by(director) %>% summarise(count = n()) # Show directors and count by each director group
-print(view)
-```
-Some of the rows have more than one director (will make maping tables)
-
-# See if country needs cleaning
-``` {r}
-view <- df %>% group_by(country) %>% summarise(count = n()) # Show country and count by each country group
-
-```
-# Many of the rows have more than one country (will make maping tables)
-
-# See if date_added needs cleaning
-``` {r}
-view <- df %>% group_by(date_added) %>% summarise(count = n()) # Show date_added and count by each date_added
-```
-# Change to date format
-``` {r}
-df$date_added <- mdy(df$date_added)
-```
-# See if release year needs cleaning
-``` {r}
-view <- df %>% group_by(release_year) %>% summarise(count = n()) # Show release_year and count by each release_year
-```
-# See if rating needs cleaning
-``` {r}
-
-view <- df %>% group_by(rating) %>% summarise(count = n()) # Show release_year and count by each release_year
-df$rating[df$rating == "PG-13" ] <- "PG"
-df$rating[df$rating == "TV-PG" ] <- "PG"
-df$rating[df$rating == "TV-14" ] <- "PG"
-df$rating[df$rating == "TV-G" ] <- "G"
-df$rating[df$rating == "TV-MA" ] <- "R"
-df$rating[df$rating == "TV-Y7" ] <- "Y"
-df$rating[df$rating == "TV-Y7-FV" ] <- "Y"
-df$rating[df$rating == "TV-Y" ] <- "Y"
-df$rating[df$rating == "NR" ] <- "UR"
-
-```
-# See if duration needs cleaning
-``` {r}
-view <- df %>% group_by(duration) %>% summarise(count = n()) # Show duration and count by each release_year
-```
-# Duration convert blanks to NA
-# Convert duration to numeric
-
-``` {r}
-df$duration[df$duration ==""] <- NA
-df <- separate(df, duration, c("duration", "duration_units"))
-df <- transform(df, duration = as.numeric(duration))
-```
-
-# See if genre needs cleaning
-``` {r}
-view <- df %>% group_by(genre) %>% summarise(count = n()) # Show genre and count by each genre
-```
-
-# See if plot needs cleaning
-``` {r}
-view <- df %>% group_by(plot) %>% summarise(count = n()) # Show plot and count by each plot
-```
-
-# See if google_score needs cleaning
-``` {r}
-view <- df %>% group_by(google_score) %>% summarise(count = n()) # Show google_score and count by each google_score
-```
-
-# Remove % and convert to numeric type
-``` {r}
-df$google_score<-gsub("%","",as.character(df$google_score))
-df <- transform(df, google_score = as.numeric(google_score))
-```
-
-Transform google_language and google_genre feature into present/absent because it was not scrappable
-``` {r}
-df$google_language <- ifelse(df$google_language =="", "absent", "present")
-view <- df %>% group_by(google_language) %>% summarise(count = n())  # Show categories and count by each category
-print(view)
-```
-``` {r}
-df$google_genre <- ifelse(df$google_genre =="", "absent", "present")
-view <- df %>% group_by(google_genre) %>% summarise(count = n())
-print(view)
-```
-
-``` {r}
-write.csv(df, "datasets/view_main_cleaned.csv", row.names=FALSE)
-df <- read.csv(file = 'datasets/view_main_cleaned.csv')
-```
 

### 2023-01-21 Packages.r

@@ -7,5 +7,6 @@
 # install.packages("lsa")
 # install.packages("ggplot2")
 # install.packages("knitr")
-install.packages("kableExtra")
-install.packages("reticulate")
+# install.packages("kableExtra")
+# install.packages("reticulate")
+install.packages("Hmisc")

### 2023-01-21 submission.Rmd
save changes

@@
 library(Hmisc)
+library(ggcorrplot)
 ```
@@
 
+## Handle Missing data
+``` {r}
+#desc <- describe(df)
+#print(desc)
+```
+
+```{r}
+feature <- new_names # retrieving all the column names
+
+NA_Count <- c(
+ toString(count_blanks('id'))
+, toString(count_blanks('type'))
+, toString(count_blanks('title'))
+, toString(count_blanks('director'))
+, toString(count_blanks('cast'))
+, toString(count_blanks('country'))
+, toString(count_blanks('date_added'))
+, toString(count_blanks('release_year'))
+, toString(count_blanks('rating'))
+, toString(count_blanks('duration'))
+, toString(count_blanks('genre'))
+, toString(count_blanks('plot'))
+, toString(count_blanks('google_score'))
+, toString(count_blanks('google_language'))
+, toString(count_blanks('google_genre'))
+, toString(count_blanks('google_plot')))
+NA_Count <- data.frame(feature, NA_Count)
+
+print(NA_Count)
+
+```
+
+Google Genre and Google Language are missing in a big proportion of rows.
+Action: Instead of removing the feature entirely, I'd like to extract some value out of it. I will transform google_language and google_genre feature into present/absent.
+
+``` {r}
+df$google_language <- ifelse(df$google_language =="", "absent", "present")
+view <- df %>% group_by(google_language) %>% summarise(count = n())
+print(view)
+```
+``` {r}
+df$google_genre <- ifelse(df$google_genre =="", "absent", "present")
+view <- df %>% group_by(google_genre) %>% summarise(count = n())
+print(view)
+```
+
 ## Fixing structural errors.
@@
 
-1. Type
+### 1. Type
 ``` {r}
@@
 
-2. director
+### 2. director
 ``` {r}
@@
 
-3. Cast
+### 3. Cast
 ``` {r}
@@
 
-3. Country
+### 4. Country
 ``` {r}
@@
 
-4. Date Added
+### 5. Date Added
 ``` {r}
@@
 
-5. Release Year
+### 6. Release Year
 ``` {r}
@@
 
-6. Rating
+### 7. Rating
 ``` {r}
@@
 df$rating[df$rating == "84 min" ] <- "UR"
+df$rating[df$rating == ""] <- "UR"
 
@@
 
-7. Duration
+### 8. Duration
 ``` {r}
@@
 df$duration_season <- ifelse(grepl("Season", df$duration),df$duration,NA)
-print(head(df, 10))
+print(head(df[,c("title","duration_min","duration_season")]))
 ```
@@
 df$duration_season <- as.numeric(df$duration_season)
-print(head(df,10))
+print(head(df[,c("title","duration_min","duration_season")]))
 ```
@@
 
-8. Genre
+### 9. Genre
 ``` {r}
@@
 
-9. Plot
+### 10. Plot
 Plot contains text data.
@@
 
-10. Google Score
+### 11. Google Score
 ``` {r}
@@
 
-11. Google Score
 ``` {r}
@@
 
-12. Google Language
+### 13. Google language
+Feature was engineered already, so it is clean.
+
+### 14. Google genre
+Feature was engineered already, so it is clean.
+
+### 15. Goolge Plot
+Goolge Plot contains text data.
+Action: Use Latent Semantic Analysis to categorize plots
+
+# Filter unwanted outliers (pending section)
+
+# Data Transformation
+
+## Mapping Tables 
+As talked about in the Data Cleaning Section above, I will build a mapping table for Cast, Director, Country and Genre. 
+This would help reflect their one to many relationship.
+
+### Build Director Mapping Table
 ``` {r}
-print(head(df$google_language), 10)
-```
-Clear that a lot of data is missing.
-Action: Extract feature from it (present/absent)
 
-Transform google_language and google_genre feature into present/absent because it was not scrappable
-view <- df %>% group_by(google_language) %>% summarise(count = n())  # Show categories and count by each category
-df$google_language <- ifelse(df$google_language =="", "absent", "present")
-print(view)
-df$google_genre <- ifelse(df$google_genre =="", "absent", "present")
-view <- df %>% group_by(google_genre) %>% summarise(count = n())
-print(view)
+director_mapping <- df %>%
+    mutate(director = strsplit(as.character(director), ",")) %>%
+    unnest(director)
 
-13. Google Genre
+director_mapping = subset(director_mapping, select = c(id, director))
+director_mapping$director <- trimws(director_mapping$director , which = c("left"))
 
-``` {r}
-print(head(df$google_language), 10)
-```
-Clear that a lot of data is missing.
-Action: Extract feature from it (present/absent)
-
-``` {r}
-#write.csv(df, "datasets/view_main_cleaned.csv", row.names=FALSE)
-#df <- read.csv(file = 'datasets/view_main_cleaned.csv')
+write.csv(director_mapping, "datasets/mapping_director.csv", row.names=FALSE)
 ```
 
-## Handle Missing data
+### Build Cast Mapping Table
+``` {r}
+cast_mapping <- df %>%
+    mutate(cast = strsplit(as.character(cast), ",")) %>%
+    unnest(cast)
 
-### Missing Data
-``` {r}
-#desc <- describe(df)
-#print(desc)
+cast_mapping = subset(cast_mapping, select = c(id, cast))
+cast_mapping$cast <- trimws(cast_mapping$cast, which = c("left"))
+write.csv(cast_mapping, "datasets/mapping_cast.csv", row.names=FALSE)
 ```
 
-```{r}
-#feature <- new_names # retrieving all the column names
-
-#NA_Count <- c(
-#  toString(count_blanks('id'))
-# , toString(count_blanks('type'))
-# , toString(count_blanks('title'))
-# , toString(count_blanks('director'))
-# , toString(count_blanks('cast'))
-# , toString(count_blanks('country'))
-# , toString(count_blanks('date_added'))
-# , toString(count_blanks('release_year'))
-# , toString(count_blanks('rating'))
-# , toString(count_blanks('duration'))
-# , toString(count_blanks('genre'))
-# , toString(count_blanks('plot'))
-# , toString(count_blanks('google_score'))
-# , toString(count_blanks('google_language'))
-# , toString(count_blanks('google_genre'))
-# , toString(count_blanks('google_plot')))
-#NA_Count <- data.frame(feature, NA_Count)
-
-#print(NA_Count)
-
-```
-
-* Validate
-
-* Step 3: Filter unwanted outliers
-
-# Cleaning each feature (sub header) 
-Look for inconsistencies, duplicates, outliers, etc. 
-Changing type and formats
-Recatagorize 
-+ id - check completeness
-+ type - summary 
-+ title - check completeness
-+ director - summary
-+ cast - summary 
-+ country - summary
-+ date_added - 
-+ release_year
-+ rating
-+ duration
-+ genre
-+ plot
-+ google_score
-+ google_language
-+ google_genre
-+ google_plot
-
-Handle missing data (sub header)
-Missing reviews (sub sub header)
-Remove rows with no data on reviews
-< code >
-
-Analysing missing datapoints (sub sub header)
-< code >
-Pretty useless to have these features
-But I transform the fields into present/absent
-Just in case it has predictive capabilities
-< code >
-
-# Mapping Tables 
-# Build Country Mapping Table
+### Build Country Mapping Table
 ``` {r}
@@
 
-# # Build Director Mapping Table
-``` {r}
-
-director_mapping <- df %>%
-    mutate(director = strsplit(as.character(director), ",")) %>%
-    unnest(director)
-
-director_mapping = subset(director_mapping, select = c(id, director))
-director_mapping$director <- trimws(director_mapping$director , which = c("left"))
-write.csv(director_mapping, "datasets/mapping_director.csv", row.names=FALSE)
-```
-
-# # Build Cast Mapping Table
-``` {r}
-cast_mapping <- df %>%
-    mutate(cast = strsplit(as.character(cast), ",")) %>%
-    unnest(cast)
-
-cast_mapping = subset(cast_mapping, select = c(id, cast))
-cast_mapping$cast <- trimws(cast_mapping$cast, which = c("left"))
-write.csv(cast_mapping, "datasets/mapping_cast.csv", row.names=FALSE)
-```
-
-# # Build Genre Mapping Table
+### Build Genre Mapping Table
 ``` {r}
@@
 
-# Trim dataset for better performance
+# Feature engineering  
+### Cast
+IMDB provides a dataset of Top 1000 Actors and Actresses based on their popularity.
+
+Analyse the IMDB actors dataset
 ``` {r}
-df = subset(df, select = -c(country,director,cast,genre) )
+IMDBActors <- read.csv(file = 'datasets/dataset_popular_actors.csv')
+print(head(IMDBActors))
+```
+The dataset  includes a numeric measure of their popularity in the column "Points".
+I clean that column so that it can be engineered, transformed and used as a feature in the main dataset.
+I write the data into a csv as a view
+
+```{r}
+IMDBActors <- separate(IMDBActors, Description, c("Points", "Description"))
+IMDBActors <- transform(IMDBActors, Points = as.numeric(Points))
 ```
 
-#Get top 100 actors and actress from IMDB list
+I do the same with the IMDB Actress dataset
+``` {r}
+IMDBActress <- read.csv(file = 'datasets/dataset_popular_actresses.csv')
 
-# Feature engineering - categories actors based on how popular they are 
-``` {r}
-popularActors <- read.csv(file = 'datasets/dataset_popular_actors.csv')
+IMDBActress <- separate(IMDBActress, Description, c("Points", "Description"))
+IMDBActress <- transform(IMDBActress, Points = as.numeric(Points))
 
-# Create new column and set default value to "top 1000"
-popularActors$rank_category <- "top 1000"
-setDT(popularActors)
-
-popularActors$rank_category[popularActors$Position < 501 ] <- "top 500"
-popularActors$rank_category[popularActors$Position < 201 ] <- "top 200"
-popularActors$rank_category[popularActors$Position < 101 ] <- "top 100"
-popularActors$rank_category[popularActors$Position < 51 ] <- "top 50"
-popularActors$rank_category[popularActors$Position < 21 ] <- "top 20"
-popularActors$rank_category[popularActors$Position < 11 ] <- "top 10"
-
-popularActors <- separate(popularActors, Description, c("Points", "Description"))
-popularActors <- transform(popularActors, Points = as.numeric(Points))
-
-# View(popularActors)
-
-write.csv(popularActors, "datasets/view_popular_actors.csv", row.names=FALSE)
 ```
 
-# Feature engineering - categories actors based on how popular they are 
-``` {r}
-popularActresses <- read.csv(file = 'datasets/dataset_popular_actresses.csv')
-
-# Create new column and set default value to "top 1000"
-popularActresses$rank_category <- "top 1000"
-setDT(popularActresses)
-
-popularActresses$rank_category[popularActresses$Position < 501 ] <- "top 500"
-popularActresses$rank_category[popularActresses$Position < 201 ] <- "top 200"
-popularActresses$rank_category[popularActresses$Position < 101 ] <- "top 100"
-popularActresses$rank_category[popularActresses$Position < 51 ] <- "top 50"
-popularActresses$rank_category[popularActresses$Position < 21 ] <- "top 20"
-popularActresses$rank_category[popularActresses$Position < 11 ] <- "top 10"
-
-# Get points from actresses
-popularActresses <- separate(popularActresses, Description, c("Points", "Description"))
-popularActresses <- transform(popularActresses, Points = as.numeric(Points))
-
-# View(popularActresses)
-
-write.csv(popularActresses, "datasets/view_popular_actresses.csv", row.names=FALSE)
-```
-
-# Feature engineering - categories directors based on how popular they are 
-``` {r}
-popularDirectors <- read.csv(file = 'datasets/dataset_popular_directors.csv')
-
-# Create new column and set default value to "top 1000"
-popularDirectors$rank_category <- "top 1000"
-setDT(popularDirectors)
-
-popularDirectors$rank_category[popularDirectors$Position < 501 ] <- "top 500"
-popularDirectors$rank_category[popularDirectors$Position < 201 ] <- "top 200"
-popularDirectors$rank_category[popularDirectors$Position < 101 ] <- "top 100"
-popularDirectors$rank_category[popularDirectors$Position < 51 ] <- "top 50"
-popularDirectors$rank_category[popularDirectors$Position < 21 ] <- "top 20"
-popularDirectors$rank_category[popularDirectors$Position < 11 ] <- "top 10"
-
-#Get points from directors
-popularDirectors <- separate(popularDirectors, Description, c("Points", "Description"))
-popularDirectors <- transform(popularDirectors, Points = as.numeric(Points))
-
-# View(popularDirectors)
-
-write.csv(popularDirectors, "datasets/view_popular_directors.csv", row.names=FALSE)
-```
-
-# Create an ephemeral in-memory RSQLite database
-#``` {r}
-
+Once that is done, I attach the points of each Actor/Actress to the cast mapping table. (Not all cast members in the table have points because they may not be in the IMDB list)
+``` {r message=FALSE}
 con <- dbConnect(RSQLite::SQLite(), ":memory:")
 
-main <- read.csv(file = 'datasets/view_main_trimmed.csv')
-cast <- read.csv(file = 'datasets/mapping_cast.csv')
-actorsPoints <- read.csv(file = 'datasets/view_popular_actors.csv')
-actressesPoints <- read.csv(file = 'datasets/view_popular_actresses.csv')
-directors <- read.csv(file = 'datasets/mapping_director.csv')
-directorsPoints <- read.csv(file = 'datasets/view_popular_directors.csv')
+dbWriteTable(con, "cast", cast_mapping)
+dbWriteTable(con, "actorsPoints", IMDBActors)
+dbWriteTable(con, "actressesPoints", IMDBActress)
 
-dbWriteTable(con, "main", main)
-dbWriteTable(con, "cast", cast)
-dbWriteTable(con, "actorsPoints", actorsPoints)
-dbWriteTable(con, "actressesPoints", actressesPoints)
-dbWriteTable(con, "directors", directors)
-dbWriteTable(con, "directorsPoints", directorsPoints)
-
-# Attach the points to the mapping table
 query <- "SELECT c.id
@@
 res <- dbSendQuery(con, query)
+
 castPointsMapping <- dbFetch(res)
-dbClearResult(res)
 
 dbWriteTable(con, "castPointsMapping", castPointsMapping)
+```
 
-#Attach the director to the mapping table
+For each Show/Movie, take the points of the most famous Actor/Actress and attach it to the main table
+```{r}
+dbWriteTable(con, "main", df)
+
+query <- "SELECT a.*
+        , CASE WHEN c.Points IS NOT NULL THEN max(c.Points)
+        ELSE 0 END AS cast_points
+        FROM main a 
+        LEFT JOIN castPointsMapping c ON a.id = c.id 
+        GROUP BY a.id"
+
+res <- dbSendQuery(con, query)
+df <- dbFetch(res)
+
+print(head(df[,c("title","cast_points")]))
+
+```
+### Directors
+I do the same for directors
+``` {r message=FALSE} 
+IMDBDirectors <- read.csv(file = 'datasets/dataset_popular_directors.csv')
+
+IMDBDirectors <- separate(IMDBDirectors, Description, c("Points", "Description"))
+IMDBDirectors <- transform(IMDBDirectors, Points = as.numeric(Points))
+
+dbWriteTable(con, "main_2", df)
+dbWriteTable(con, "directorsPoints", IMDBDirectors)
+dbWriteTable(con, "director", director_mapping)
+
 query <- "SELECT a.id
@@
                 ELSE 0 END AS Points
-                FROM directors a
+                FROM director a
                 LEFT JOIN directorsPoints d ON a.director = d.Name"
@@
 query <- "SELECT a.*
-        , CASE WHEN c.Points IS NOT NULL THEN max(c.Points)
-        ELSE 0 END AS cast_points
         , CASE WHEN d.Points IS NOT NULL THEN max(d.Points)
         ELSE 0 END AS director_points
-        FROM main a 
-        LEFT JOIN castPointsMapping c ON a.id = c.id 
+        FROM main_2 a 
         LEFT JOIN directorPointsMapping d ON a.id = d.id 
@@
 dbClearResult(res)
-#```
 
-# Seperate google_scores into bins
-#``` {r}
-# df$google_scoreClass <- cut(df$google_score, breaks=c(0,60,70,80,90,100), labels=c("0-60","61-70","71-80","81-90","90-100"))
+print(head(df[,c("title","director_points")]))
+```
 
-write.csv(df, "datasets/view_main_features.csv", row.names=FALSE)
+Before carrying out further analysis, I disconnect from SQLite I write the main dataframe into a csv 
+``` {r}
+dbDisconnect(con)
+write.csv(df, "datasets/view_main_cleaned.csv", row.names=FALSE)
+```
 
-dbDisconnect(con)
-#```
-
-# Latent Semantic Analysis of Plot and google plot data
-``` {r}
-
-```
+# Feature Engineering -  Latent Semantic Analysis of Plot and google plot data
 # load data
@@
 #```
+
+# Exploratory Data Analysis
+
+### Corelation between numeric features
+Before we get started, it would be useful to know how correlated the features are. I do this for the numeric features. 
+``` {r}
+numeric_features <-  select_if(df, is.numeric)
+corr<- cor(numeric_features)
+ggcorrplot(corr)
+plot()
+```
+
+### Findings
+* Release Year and Google Score are slightly negatively correlated
+* Director Points and and Google Score are also slightly positively correlated
+* Cast Points and and Google Score are also slightly positively correlated 
+* Release Year and Director Points are slightly negatively correlated
+* Release Year and Cast Points are slightly negatively correlated

### 2023-01-23 submission.Rmd
save work

@@
         , netflixData.duration
-        , netflixData.listed_in
         , netflixData.description
@@
         , "duration"
-        , "genre"
         , "plot"
@@
 , toString(count_blanks('duration'))
-, toString(count_blanks('genre'))
 , toString(count_blanks('plot'))
@@
 
+```
+
+``` {r}
+missing.values <- df %>%
+    gather(key = "key", value = "val") %>%
+    mutate(is.missing = is.na(val)) %>%
+    group_by(key, is.missing) %>%
+    summarise(num.missing = n()) %>%
+    filter(is.missing==T) %>%
+    select(-is.missing) %>%
+    arrange(desc(num.missing))
+
+print(missing.values)
 ```
@@
 ```
-Some shows originated from several different countries.
-Action: Similar to what will be done with the Director and Cast Feature, I will make mapping tables and use feature engineering to capture this variable.
+Some shows originated from several different countries. However, the countries seem to be in the order of influence.
+Action: Take the first country on the list.
+
+``` {r}
+df$country <- sub("\\,.*", "", df$country)
+```
 
@@
 print(typeof(df$date_added))
+print(df$date_added)
+
 ```
@@
 ``` {r}
-df$date_added <- mdy(df$date_added)
+#df$date_added <- mdy(df$date_added)
+#print(df$date_added )
 ```
@@
 
-### 9. Genre
-``` {r}
-view <- df %>% group_by(genre) %>% summarise(count = n()) # Show genre and count by each genre
-print(view)
-```
-Some of the rows have more than one genre. 
-Action: In the next Feature Engineering Section, I will make mapping tables and use feature engineering to capture this variable
-
 ### 10. Plot
@@
 write.csv(cast_mapping, "datasets/mapping_cast.csv", row.names=FALSE)
-```
-
-### Build Country Mapping Table
-``` {r}
-
-country_mapping <- df %>%
-    mutate(country = strsplit(as.character(country), ",")) %>%
-    unnest(country)
-
-country_mapping = subset(country_mapping, select = c(id, country))
-country_mapping$country <- trimws(country_mapping$country, which = c("left"))
-
-write.csv(country_mapping, "datasets/mapping_country.csv", row.names=FALSE)
-```
-
-### Build Genre Mapping Table
-``` {r}
-genre_mapping <- df %>%
-    mutate(genre = strsplit(as.character(genre), ",")) %>%
-    unnest(genre)
-
-genre_mapping = subset(genre_mapping, select = c(id, genre))
-genre_mapping$cast <- trimws(genre_mapping$genre, which = c("left"))
-write.csv(genre_mapping, "datasets/mapping_genre.csv", row.names=FALSE)
 ```
@@
 dbDisconnect(con)
+print(head(df,10))
+
+df = subset(df, select = -c(cast,director) )
+
 write.csv(df, "datasets/view_main_cleaned.csv", row.names=FALSE)
@@
 # Exploratory Data Analysis
+# https://shopify.engineering/conducting-exploratory-data-analysis
+
+### Feature Description
+
+1. Type : Type of Netflix Show (Movie or TV Show)
+2. Title: Name of the Netflix Show
+3. Director : List of directors of the show
+4. Cast: List of casts of the show
+5. Country: List of countries relating to the show
+6. Date Added: Date the show was put on Netflix
+7. Release Year: Year the show was first released
+8. Genre: List of genres of the show 
+9. Plot: Description of the plot of the show
+10. Google Score: Displayed on Google as the percentage of viewers that liked a show
+11. Google Genre: Whether or not Genre is absent/present in the google search
+12. Google Language: Whether or not Language is absent/present in the google search
+13. Google Plot: Plot of the show according to Google
+14. Duration Minutes: Duration of the movie in minutes
+15. Duration Seasons: Durationg of the TV show in terms of how many seasons it has
+16. Cast Points: Level of popularity of the most famous cast member of the show according to IMDB
+17. Director Points: Level of popularity of the most famous director of the show according to IMDB
+18. LSA category: Category of the show according to the LSA algorithm
+
+Dependent Feature:
+Google Score:
+
+Independent Features:
+Type, Date Added, Release Year, Google Genre, Google Language, Duration Minutes, Duration Seasons, Cast Points, Director Points, LSA Category
+
+Features not directly for Analysis:
+Title, Director, Cast, Country, Genre, Plot, Google Plot
+
+### Among the Independent Features, What are the Categorical, discrete and continuous features
+
+Categorical: Type, LSA Category
+
+Discrete: Date Added, Release Year, Google Genre, Google Language, Duration Seasons
+
+Continuous: Duration Minutes, Cast Points, Director Points
+
+### Distribution of the features
+
+1. Type
+```{r}
+ggplot(df, aes(x = type)) +  # Plot with values on top
+  geom_bar() 
+plot()
+```
+2. LSA
+
+3. Date Added
+```{r}
+ggplot(df, aes(x = date_added)) +
+    geom_density()
+plot()
+```
+
+### Find outliers
+
+### Significant Correlations
 
@@
 Before we get started, it would be useful to know how correlated the features are. I do this for the numeric features. 
-``` {r}
+<!-- ``` {r}
 numeric_features <-  select_if(df, is.numeric)
-corr<- cor(numeric_features)
+corr <- cor(numeric_features)
 ggcorrplot(corr)
 plot()
-```
+``` -->
 
@@
 * Release Year and Cast Points are slightly negatively correlated
+
+#

### 2023-01-23 Packages.r

@@ -9,4 +9,5 @@
 # install.packages("knitr")
 # install.packages("kableExtra")
 # install.packages("reticulate")
-install.packages("Hmisc")
+# install.packages("Hmisc")
+install.packages("ggcorrplot")

### 2023-01-23 submission.Rmd
save work

@@
 ---
-
-```{r echo=FALSE, out.width = '100%'}
-knitr::include_graphics("netflixHomepage.JPG")
-```
 
@@
 library(ggcorrplot)
+library(forcats)
 ```
@@
 netflixData <- read.csv(file = 'datasets/dataset_main.csv')
-```
-```{r echo=FALSE}
-# FOR Displaying results
-# temp = head(netflixData, 10)
-# temp %>%
-#   kbl() %>%
-#   kable_styling() %>%
-#   column_spec(1, width = "10cm") %>%
-#   scroll_box(width = "1000px", height = "500px")
 ```
@@
 # Cleaning the data
-
 ## Removing duplicates or irrelevant observations
-## Dealing with duplicates 
+### Dealing with duplicates 
 Checking if there are any duplicated Netflix Shows
@@
 
-## Handle Missing data
-``` {r}
-#desc <- describe(df)
-#print(desc)
-```
-
+### Handle Missing data
+Lets see what data is missing:
 ```{r}
@@
 print(NA_Count)
-
 ```
@@
 
-### 2. director
+### 2. Director
 ``` {r}
@@
 df$country <- sub("\\,.*", "", df$country)
+
+view <- df %>% group_by(country) %>% summarise(count = n())
+print(view)
+```
+Some Countries appear very few times 
+Action: I will group them into an "Others" category if count is less than 50
+``` {r}
+df <- df %>% 
+    group_by(country) %>% 
+    mutate(country = ifelse(n()>50, country, 'Others'))
 ```
@@
 print(view)
-print(typeof(df$date_added))
-print(df$date_added)
-
 ```
-Date Added is in the character format.
-Action: Change this to date format
-``` {r}
-#df$date_added <- mdy(df$date_added)
-#print(df$date_added )
-```
+Date Added looks good
+Action: None
 
@@
 ```
-
 Drop duration column
@@
 ## Mapping Tables 
-As talked about in the Data Cleaning Section above, I will build a mapping table for Cast, Director, Country and Genre. 
+As talked about in the Data Cleaning Section above, I will build a mapping table for Cast and Director
+
 This would help reflect their one to many relationship.
@@
 
-For each Show/Movie, take the points of the most famous Actor/Actress and attach it to the main table
+For each Show/Movie, if there are points attached to at least one of the actors/actresses, I give the new variable cast_points the value "known", otherwise, it is labelled as "unknown".
 ```{r}
@@
 query <- "SELECT a.*
-        , CASE WHEN c.Points IS NOT NULL THEN max(c.Points)
-        ELSE 0 END AS cast_points
+        , CASE WHEN c.Points IS NOT NULL THEN 'known'
+        ELSE 'unknown' END AS cast_points
         FROM main a 
@@
 query <- "SELECT a.*
-        , CASE WHEN d.Points IS NOT NULL THEN max(d.Points)
-        ELSE 0 END AS director_points
+        , CASE WHEN d.Points IS NOT NULL THEN 'known'
+        ELSE 'unknown' END AS director_points
         FROM main_2 a 
@@
 
+Drop Director and Cast Column
+```{r}
+df = subset(df, select = -c(cast,director) )
+```
+
 Before carrying out further analysis, I disconnect from SQLite I write the main dataframe into a csv 
@@
 dbDisconnect(con)
-print(head(df,10))
-
-df = subset(df, select = -c(cast,director) )
-
 write.csv(df, "datasets/view_main_cleaned.csv", row.names=FALSE)
@@
 
+## Data Preview
+Here is what the dataset looks like now after cleaning
+``` {r echo=FALSE}
+temp = head(df, 10)
+temp %>%
+  kbl() %>%
+  kable_styling() %>%
+  column_spec(1, width = "10cm") %>%
+  scroll_box(width = "1000px", height = "500px")
+```
+
 # Feature Engineering -  Latent Semantic Analysis of Plot and google plot data
-# load data
+#### load data
 
@@
 #```
-# Convert data to corpus
+#### Convert data to corpus
 #``` {r}
@@
 
-# Remove special characters, case, punctuation and numbers
+#### Remove special characters, case, punctuation and numbers
 #``` {r}
@@
 
-# Remove stop words
+#### Remove stop words
 #``` {r}
@@
 
-# Remove white space
+#### Remove white space
 #``` {r}
@@
 
-# Stemming
+#### Stemming
 #``` {r}
@@
 
-# Term document matrix
+#### Term document matrix
 #``` {r}
@@
 
-# View top 5 most frequently occuring term
+#### View top 5 most frequently occuring term
 #``` {r}
@@
 
-# Weighting 
+#### Weighting 
 #``` {r}
@@
 
-# Latent Semantic Analysis
+#### Latent Semantic Analysis
 #``` {r}
@@
 
-# Varimax Rotation
+#### Varimax Rotation
 #``` {r}
@@
 
-# Interreting Term and Document Matrices
+#### Interreting Term and Document Matrices
 #``` {r}
@@
 Dk.thresholded <- as.data.table(threshold.loadings.table(sort.loadings.table(Dk.rotated),q=1))
-# print(Dk.thresholded[,.(item,max.factor,max.value)])
+print(Dk.thresholded[,.(item,max.factor,max.value)])
 write.csv(Dk.thresholded[,.(item,max.factor,max.value)],"datasets/dk.csv", row.names=FALSE)
 #```
+###biplot
 #``` {r}
@@
 
-#``` {r}
-
+``` {r}
 con <- dbConnect(RSQLite::SQLite(), ":memory:")
 
-main <- read.csv(file = 'datasets/view_main_features.csv')
+main <- read.csv(file = 'datasets/view_main_cleaned.csv')
 lsa <- read.csv(file = 'datasets/lsa_2.csv')
 
-lsa$item <- sub("^", "s", lsa$item )
+lsa$item <- sub("^", "s", lsa$item)
 
@@
 
-query <- "SELECT m.*, l.*
+query <- "SELECT m.*, l.[max.factor] as lsa_value
                 FROM main m
@@
 dbClearResult(res)
-setDT(df)
-View(df)
+
+df = subset(df, select = -c(plot,google_plot))
 
@@
 dbDisconnect(con)
-#```
+```
+# Data Preview 
+``` {r echo=FALSE}
+temp = head(df, 10)
+temp %>%
+  kbl() %>%
+  kable_styling() %>%
+  column_spec(1, width = "10cm") %>%
+  scroll_box(width = "1000px", height = "500px")
+```
 
@@
 
-1. Type
-```{r}
-ggplot(df, aes(x = type)) +  # Plot with values on top
-  geom_bar() 
-plot()
+```{r echo=FALSE, out.width = '50%'}
+knitr::include_graphics("Type Distribution.JPG")
 ```
-2. LSA
+```{r echo=FALSE, out.width = '50%'}
+knitr::include_graphics("DirectorDist.JPG")
+```
+```{r echo=FALSE, out.width = '50%'}
+knitr::include_graphics("CastDist.JPG")
+```
+```{r echo=FALSE, out.width = '50%'}
+knitr::include_graphics("DateAddedDist.JPG")
+```
 
-3. Date Added
-```{r}
-ggplot(df, aes(x = date_added)) +
-    geom_density()
-plot()
-```
+<iframe src=" https://public.tableau.com/views/DistributionNetflix/TypeDist?:language=en-US&publish=yes&:display_count=n&:origin=viz_share_link:showVizHome=no&:embed=true"
+ width="645" height="955"></iframe>
 

### 2023-01-23 Packages.r

@@ -10,4 +10,5 @@
 # install.packages("kableExtra")
 # install.packages("reticulate")
 # install.packages("Hmisc")
-install.packages("ggcorrplot")
+# install.packages("ggcorrplot")
+install.packages("forcats")

### 2023-02-18 python files/PythonDataScraping.py
image scraping

@@ -72,3 +72,4 @@ get_googleInfo("Squid Game")
 # data = pd.read_csv('netflix_titles.csv')
 # goolgeInfo = data['title'].apply(get_googleInfo)
 # goolgeInfo.to_csv('googleInfo.csv', encoding='utf-8', index=False)
+

### 2023-02-18 submission.Rmd
commit

@@
 
-# About
+# Section 1
+
+### Dataset
+The Kaggle Netflix dataset provides us with a list of Netflix Shows along with information such as the year it was added, duration, cast, description etc. \
+
+There are altogether 8807 Netflix Shows in this dataset.\
+
+We also supplement the dataset with several features that were scrapped from google.
+
+### Columns in dataset
+```{r echo=FALSE, out.width = '70%'}
+knitr::include_graphics("Data Description.JPG")
+```
+
+### About
 This project is about analysing what makes a show on Netflix more likeable?
@@
 
-This project aims to answer such questions via going through the whole process of creating a machine learning model
+These answers will help us decide what shows to are more likely to be worth while watching on Netlix and save us valuable time.
 
-# Packages
+This project aims to answer such questions by running a Multiregression model on Netflix data.
+
+### Algorithm Choice
+
+To solve this problem, I will use the multivariate regression model. \
+I use this model to evaluate the correlation between the features in the data set and Google Review Score.\
+\
+I chose this algorithm because the dependent feature (Google Review Score) is a continuous feature.\
+Furthermore, both numeric and categorical features can easily be integrated with this model. \
+\
+From the multi regression model results, we can determine the degree of influence many different features have on a dependent features.\
+Moreover, the effect of each feature can be seen while the effect of the other features are held constant.\
+Specifically, a slope coefficient and it’s statistical significance is gained for each feature in the dataset.\
+\
+Although causality may not be implied with the results, having a sense of what to features of a show to look out for on Netflix could still help us with choosing what to watch.\ 
+With that being said, I am aware of the disadvantages that come with this model.\
+Some of the problems that I am prepared to face are overfitting, bias-variance dilemma, multicollinearity and the curse of dimensionality
+
+# Section 2 
+## Loading Packages
 Before we get started. We will load all the relevant Pacakages
@@
 
-# Getting Data
+## Getting Data
 
@@
 Apply data scraping function on all movie/show titles in dataset. 
-Once all the information has been scraped, I write it into a csv file (full code in GitHub).
+Once all the information has been scraped, I write it into a csv file.
 ``` {python eval = FALSE}
-# data = pd.read_csv('netflix_titles.csv')
-# goolgeInfo = data['title'].apply(get_googleInfo)
-# goolgeInfo.to_csv('googleInfo.csv', encoding='utf-8', index=False)
-print("hi")
+## This batch of code takes ages, do not run it
+data = pd.read_csv('netflix_titles.csv')
+goolgeInfo = data['title'].apply(get_googleInfo)
+goolgeInfo.to_csv('datasets/dataset_googleScraped.csv', encoding='utf-8', index=False)
 ```
@@
         , netflixData.description
+        , netflixData.listed_in
         , googleData.Likes
@@
 
-# Previewing Raw Data
-## Renaming Columns
+## Previewing Raw Data
+### Renaming Columns
 I rename the columns because some of them had the same names. 
@@
         , "plot"
+        , "listedIn"
         , "google_score"
@@
 ```
-## Data Preview
+### Data Preview
 Here is what the dataset looks like now, we can see all the features that will be used:
@@
 
-# Cleaning the data
-## Removing duplicates or irrelevant observations
+## Cleaning the data
 ### Dealing with duplicates 
@@
 ``` {r}
-print(df[duplicated(df$title),])
+duplicated <-df[duplicated(df$title),]
+print(duplicated$title)
 ```
@@
 
-### Drop rows
+#### Drop rows
 Any Netflix Show which does not have a Google Review Score (crucial dependent variable) is an irrelevant observation since it cannot be used for Analysis.
@@
 , toString(count_blanks('plot'))
+, toString(count_blanks('listedIn'))
 , toString(count_blanks('google_score'))
@@
 print(NA_Count)
-```
-
-``` {r}
-missing.values <- df %>%
-    gather(key = "key", value = "val") %>%
-    mutate(is.missing = is.na(val)) %>%
-    group_by(key, is.missing) %>%
-    summarise(num.missing = n()) %>%
-    filter(is.missing==T) %>%
-    select(-is.missing) %>%
-    arrange(desc(num.missing))
-
-print(missing.values)
 ```
@@
 
-## Fixing structural errors.
+### Fixing structural errors.
 Structural errors are when you measure or transfer data and notice strange naming conventions, typos, or incorrect capitalization.
@@
 
-### 1. Type
+#### 1. Type
 ``` {r}
@@
 ```
-The type feature looks clean, no action will be taken on it.
+The type feature looks clean, no action will be taken on it.\
 Action: None
 
-### 2. Director
+#### 2. Director
 ``` {r}
@@
 ```
-Some of the rows have more than one director. 
+Some of the rows have more than one director. \
 Action: In the next Feature Engineering Section, I will make mapping tables and use feature engineering to capture this variable
 
-### 3. Cast
+#### 3. Cast
 ``` {r}
@@
 ```
-As expected, many Shows have more than one cast member. 
+As expected, many Shows have more than one cast member. \
 Action: Similar to what will be done with the Director Feature, I will make mapping tables and use feature engineering to capture this variable
 
-### 4. Country
+#### 4. Country
 ``` {r}
@@
 ```
-Some shows originated from several different countries. However, the countries seem to be in the order of influence.
+Some shows originated from several different countries. However, the countries seem to be in the order of influence.\
 Action: Take the first country on the list.
@@
 ```
-Some Countries appear very few times 
-Action: I will group them into an "Others" category if count is less than 50
+Some Countries appear very few times \
+Also, we don't want too many categories to avoid overfitting and the curse of dimensionality.\
+Action: I will group them into an "Others" category if count is less than 100. 
 ``` {r}
@@
     group_by(country) %>% 
-    mutate(country = ifelse(n()>50, country, 'Others'))
+    mutate(country = ifelse(n()>100, country, 'Others'))
 ```
 
-### 5. Date Added
+#### 5. Date Added
 ``` {r}
@@
 ```
-Date Added looks good
+Date Added looks good\
 Action: None
 
-### 6. Release Year
+#### 6. Release Year
 ``` {r}
@@
 ```
-Release Year has the integer type. No noticable structural error.
+Release Year has the integer type. No noticable structural error.\
 Action: None
 
-### 7. Rating
+#### 7. Rating
 ``` {r}
@@
 ```
-There are several categories which have the same meaning.
+There are several categories which have similar meaning. \
+Similar to the the Country feature, we don't want too many categories to avoid overfitting and the curse of dimensionality.\
 Action: Consolidate the categories
@@
 
-### 8. Duration
+#### 8. Duration
 ``` {r}
@@
 ```
-Durations with two different units are in the same feature. Also, we can remove their units to make it integers.
+Durations with two different units are in the same feature. Also, we can remove their units to make it integers.\
 Action: Split column into two different types of durations, remove units
@@
 
-### 10. Plot
-Plot contains text data.
+#### 9. Plot
+Plot contains text data.\
 Action: Use Latent Semantic Analysis to categorize plots
 
-### 11. Google Score
+#### 10. Listed In
+``` {r}
+view <- df %>% group_by(listedIn) %>% summarise(count = n()) # Show duration and count by each release_year
+print(view)
+```
+Contains many different category tags for each show, there is too many different combinations.\
+Using this feature alone would give us a few hundred features. Again, we want to avoid overfitting and the curse of dimensionality.\
+At the same time, there may be lots of useful information in the tags.
+Action: Attach Listend In tags to Plot for Latent Semantic Analysis
+
+#### 11. Google Score
 ``` {r}
@@
 ```
-Symbol exist and type is character
+Symbol exist and type is character.\
 Action: remove symbol and convert type to numeric
@@
 
-### 13. Google language
+#### 13. Google Language
 Feature was engineered already, so it is clean.
 
-### 14. Google genre
+#### 14. Google Genre
 Feature was engineered already, so it is clean.
 
-### 15. Goolge Plot
-Goolge Plot contains text data.
+#### 15. Goolge Plot
+Goolge Plot contains text data.\
 Action: Use Latent Semantic Analysis to categorize plots
 
-# Filter unwanted outliers (pending section)
+## Data Transformation
 
-# Data Transformation
-
-## Mapping Tables 
-As talked about in the Data Cleaning Section above, I will build a mapping table for Cast and Director
+### Mapping Tables 
+As talked about in the Data Cleaning Section above, I will build a mapping table for Cast and Director.\
 
@@
 
-### Build Director Mapping Table
+#### Build Director Mapping Table
 ``` {r}
@@
 
-### Build Cast Mapping Table
+#### Build Cast Mapping Table
 ``` {r}
@@
 
-# Feature engineering  
+## Feature engineering  
 ### Cast
-IMDB provides a dataset of Top 1000 Actors and Actresses based on their popularity.
+IMDB provides a dataset of Top 1000 Actors and Actresses based on their popularity. \
 
@@
 ```
-The dataset  includes a numeric measure of their popularity in the column "Points".
-I clean that column so that it can be engineered, transformed and used as a feature in the main dataset.
+The dataset  includes a numeric measure of their popularity in the column "Points".\
+I clean that column so that it can be engineered, transformed and used as a feature in the main dataset.\
 I write the data into a csv as a view
@@
 Once that is done, I attach the points of each Actor/Actress to the cast mapping table. (Not all cast members in the table have points because they may not be in the IMDB list)
-``` {r message=FALSE}
+``` {r message=FALSE, warning=FALSE}
 con <- dbConnect(RSQLite::SQLite(), ":memory:")
@@
 ```
-
-For each Show/Movie, if there are points attached to at least one of the actors/actresses, I give the new variable cast_points the value "known", otherwise, it is labelled as "unknown".
+There are many ways to engineer a new feature with this new dataset. 
+For simplicity and interpretability, if there are points attached to at least one of the actors/actresses in a show, I give the new feature cast_points the value "known", otherwise, it is labelled as "unknown".
 ```{r}
@@
 ### Directors
-I do the same for directors
-``` {r message=FALSE} 
+Similar to what was done with the cast, I do the same for directors
+``` {r message=FALSE, warning=FALSE} 
 IMDBDirectors <- read.csv(file = 'datasets/dataset_popular_directors.csv')
@@
 
-# Feature Engineering -  Latent Semantic Analysis of Plot and google plot data
+## Feature Engineering -  Latent Semantic Analysis of Plot and google plot data
 #### load data
+The features plot, google plot and listedIn provides us with text data which we could not use directly as features.\
+To extract valuable information from it, I use a technique in natural language processing.\
+Latent Semantic Analysis (LSA) Uses the statistical approach to identify the association among the words in a document.\
+This means we can use LSA to identify the similarity between Netflix Shows base on the text in their plot, google plot and listed In tags.
+Using LSA, we will also group similary Shows and use these groups in the Multiregression mode.
 
-#``` {r}
-main <- read.csv(file = 'datasets/view_main_features.csv')
-main$plot_combined <- paste(main$plot,main$google_plot)
-#```
+``` {r}
+main <- read.csv(file = 'datasets/view_main_cleaned.csv')
+main$plot_combined <- paste(main$plot,main$listedIn,main$google_plot)
+```
 #### Convert data to corpus
-#``` {r}
+``` {r}
 corpus <- Corpus(VectorSource(main$plot_combined))
-#```
+```
 
 #### Remove special characters, case, punctuation and numbers
-#``` {r}
+``` {r message=FALSE, warning=FALSE}
 
@@
 corpus <- tm_map(corpus, content_transformer(tolower))
-#```
+```
 
 #### Remove stop words
-#``` {r}
+``` {r message=FALSE, warning=FALSE}
 corpus <- tm_map(corpus, removeWords, stopwords("english"))
-#```
+```
 
 #### Remove white space
-#``` {r}
+``` {r message=FALSE, warning=FALSE}
 corpus <- tm_map(corpus, stripWhitespace)
-#```
+```
 
 #### Stemming
-#``` {r}
+``` {r message=FALSE, warning=FALSE}
 corpus <- tm_map(corpus, stemDocument)
-#```
+```
 
 #### Term document matrix
-#``` {r}
+``` {r message=FALSE, warning=FALSE}
 tdm <- TermDocumentMatrix(corpus)
-#```
+```
 
-#### View top 5 most frequently occuring term
-#``` {r}
+#### View top 20 most frequently occuring term
+``` {r }
 tdmMatrix <- as.matrix(tdm)
@@
 d <- data.frame(word=names(v),freq=v)
-print(head(d,5))
-#```
+print(head(d,20))
+```
 
 #### Weighting 
-#``` {r}
+``` {r}
 tdm2 <- as.textmatrix(as.matrix(tdm))
 tdm.weighted <- lw_logtf(tdm2)
-print(tdm.weighted)
-#```
+```
 
 #### Latent Semantic Analysis
-#``` {r}
-lsa <- lsa(tdm.weighted, dims=10)
+``` {r eval=FALSE}
+lsa <- lsa(tdm.weighted, dims=6)
 
@@
 Dk <- lsa$dk 
-#```
+```
 
 #### Varimax Rotation
-#``` {r}
+``` {r eval=FALSE}
 Tk.varimax <- varimax(Tk)
@@
 Tk.rotated <- Tk %*% Tk.varimax$rotmat 
-#```
+```
 
 #### Interreting Term and Document Matrices
-#``` {r}
+``` {r eval=FALSE}
 
@@
 write.csv(Dk.thresholded[,.(item,max.factor,max.value)],"datasets/dk.csv", row.names=FALSE)
-#```
-###biplot
-#``` {r}
-biplot <- function(Tk,Dk,xdim,ydim,Tk.scale=1,...){
-    print("made it")
-    Tk[,type:="Terms"]
-    Dk[,type:="Title"]
-    biplot.data <- rbindlist(list(Tk,Dk))
-    setnames(biplot.data,xdim,"F1")
-    setnames(biplot.data,ydim,"F2")
-    biplot.data[type=="Terms",F1:=F1*Tk.scale]
-    biplot.data[type=="Terms",F2:=F2*Tk.scale]
-    ggplot(biplot.data, aes(x=F1, y=F2, label=item, col=type)) + geom_text()
-}
+```
+Below shows a collection of words from the LSA analysis.\
+ Words of the same group have the same colour
+```{r echo=FALSE, out.width = '100%'}
+knitr::include_graphics("LSA_word_grouping.JPG")
+```
+These Are my findings from the groupings:\
+Group 1 (blue) love, romance and marriage\
+Group 2 (orange) crime and investigation\
+Group 3 (green) comedy\
+Group 4 (red) action, adventure and sci-fi\
+Group 5 (purple) documentaries and docuseries\
+Group 6 (grey) children\
 
-plot(biplot(Tk=Tk.thresholded,Dk=Dk.thresholded, xdim="V1", ydim="V2", Tk.scale=2))
-#```
-
-# Join LSA data to main dataframe
+#### Join LSA data to main dataframe
 
@@
 main <- read.csv(file = 'datasets/view_main_cleaned.csv')
-lsa <- read.csv(file = 'datasets/lsa_2.csv')
+lsa <- read.csv(file = 'datasets/dk.csv')
 
@@
 
-df = subset(df, select = -c(plot,google_plot))
+df = subset(df, select = -c(plot,google_plot,listedIn))
 
@@
 ```
-# Data Preview 
+#### Data Preview 
 ``` {r echo=FALSE}
@@
 
-# Machine learning model Multi Regressions
-#``` {r}
-main <- read.csv(file = 'datasets/view_main_lsa.csv')
-
-main$date_added <- as.Date(as.character(main$date_added))
-main$max.factor<-as.character(main$max.factor)
-
-main = subset(main, select = -c(plot,google_plot,id,title,duration_units,item,max.value))
-
-row.number <- sample(1:nrow(main), 0.5*nrow(main))
-train = main[row.number,]
-test = main[-row.number,]
-
-print("running regression.....")
-model1 = lm(log(google_score)~., data=train)
-print(summary(model1))
-#```
-
-# Exploratory Data Analysis
-# https://shopify.engineering/conducting-exploratory-data-analysis
+## Exploratory Data Analysis
 
@@
 2. Title: Name of the Netflix Show
-3. Director : List of directors of the show
-4. Cast: List of casts of the show
-5. Country: List of countries relating to the show
-6. Date Added: Date the show was put on Netflix
-7. Release Year: Year the show was first released
-8. Genre: List of genres of the show 
-9. Plot: Description of the plot of the show
-10. Google Score: Displayed on Google as the percentage of viewers that liked a show
-11. Google Genre: Whether or not Genre is absent/present in the google search
-12. Google Language: Whether or not Language is absent/present in the google search
-13. Google Plot: Plot of the show according to Google
-14. Duration Minutes: Duration of the movie in minutes
-15. Duration Seasons: Durationg of the TV show in terms of how many seasons it has
-16. Cast Points: Level of popularity of the most famous cast member of the show according to IMDB
-17. Director Points: Level of popularity of the most famous director of the show according to IMDB
-18. LSA category: Category of the show according to the LSA algorithm
+3. Country: List of countries relating to the show
+4. Date Added: Date the show was put on Netflix
+5. Release Year: Year the show was first released
+6. Rating: List of genres of the show 
+7. Google Score: Displayed on Google as the percentage of viewers that liked a show
+8. Google Genre: Whether or not Genre is absent/present in the google search
+9. Google Language: Whether or not Language is absent/present in the google search
+10. Duration Minutes: Duration of the movie in minutes
+11. Duration Seasons: Durationg of the TV show in terms of how many seasons it has
+12. Cast Points: Whether or not the cast members are famous according to IMDB
+13. Director Points: Whether or not the directors are famous according to IMDB
+14. LSA Value: Category of the show according to the LSA algorithm
 
-Dependent Feature:
-Google Score:
+Dependent Feature: Google Score
 
-Independent Features:
-Type, Date Added, Release Year, Google Genre, Google Language, Duration Minutes, Duration Seasons, Cast Points, Director Points, LSA Category
+### Distribution Analysis of each Feature
+Click through the tableau story to see how each feature is distributed:
 
-Features not directly for Analysis:
-Title, Director, Cast, Country, Genre, Plot, Google Plot
+<iframe src=" https://public.tableau.com/views/NetflixDistribution/Story1?:language=en-GB&publish=yes&:display_count=n&:origin=viz_share_link
+:showVizHome=no&:embed=true"
+ width="1050" height="870"></iframe>
 
-### Among the Independent Features, What are the Categorical, discrete and continuous features
+### Bivariate Analysis - Significant Correlations
+Click through the tableau story to see how each feature is correlated with Google Scores:
+<iframe src=" https://public.tableau.com/views/BivariateAnalysisNetflix/Story1?:language=en-GB&publish=yes&:display_count=n&:origin=viz_share_link
+:showVizHome=no&:embed=true"
+ width="1050" height="850"></iframe>
 
-Categorical: Type, LSA Category
+### Feature Selection
+The duration of a show both in terms of minutes and seasons seem to have a very strong positive correlation with the likeability of a show.\
+Since many popular and highly rated shows will more likely renew for a next season, there is a high chance of reverse causality.\
+Because of this, I remove duration_season from the multi regression analysis.
 
-Discrete: Date Added, Release Year, Google Genre, Google Language, Duration Seasons
+Similarly, there is a high chance that if a show is very popular, google is more likely to list it's genre and language.
+To mitigate the effects of reverse causality on the model, I remove google genre and google language from the model.
 
-Continuous: Duration Minutes, Cast Points, Director Points
+## Machine learning with Multi Regression
 
-### Distribution of the features
-
-```{r echo=FALSE, out.width = '50%'}
-knitr::include_graphics("Type Distribution.JPG")
-```
-```{r echo=FALSE, out.width = '50%'}
-knitr::include_graphics("DirectorDist.JPG")
-```
-```{r echo=FALSE, out.width = '50%'}
-knitr::include_graphics("CastDist.JPG")
-```
-```{r echo=FALSE, out.width = '50%'}
-knitr::include_graphics("DateAddedDist.JPG")
+``` {r}
+main <- read.csv(file = 'datasets/view_main_lsa.csv')
 ```
 
-<iframe src=" https://public.tableau.com/views/DistributionNetflix/TypeDist?:language=en-US&publish=yes&:display_count=n&:origin=viz_share_link:showVizHome=no&:embed=true"
- width="645" height="955"></iframe>
+```{r  echo=FALSE}
+main$date_added <- mdy(main$date_added)
+main$lsa_value <- as.character(main$lsa_value)
+main$duration_min <- main$duration_min %>% replace(is.na(.), 0)
+main$duration_season <- main$duration_season %>% replace(is.na(.), 0)
+```
 
-### Find outliers
+Score as a function of all the features
+```{r}
+main = subset(main, select = -c(id,title,duration_season, google_genre, google_language))
 
-### Significant Correlations
-
-### Corelation between numeric features
-Before we get started, it would be useful to know how correlated the features are. I do this for the numeric features. 
-<!-- ``` {r}
-numeric_features <-  select_if(df, is.numeric)
-corr <- cor(numeric_features)
-ggcorrplot(corr)
-plot()
-``` -->
+model = lm(log(google_score)~., data=main)
+print(summary(model))
+```
 
 ### Findings
-* Release Year and Google Score are slightly negatively correlated
-* Director Points and and Google Score are also slightly positively correlated
-* Cast Points and and Google Score are also slightly positively correlated 
-* Release Year and Director Points are slightly negatively correlated
-* Release Year and Cast Points are slightly negatively correlated
 
-#
+Positively Correlated with significance \
+* TV Show\
+* Japan, South Korea,United Kingdom, United States\
+* Duration minutes\
+
+Negatively Correlated with significance \
+* Release Year\
+* Rating Y\
+
+These findings suggest that TV shows are more likeable than movies when other features are held constant.\
+Furthermore, shows from Japan, South Korea, United Kingdom, United States also do better.\
+The longer the movie, the higher it's score\
+
+On the other hand, there is a significant negavite correlation between a show's likeability and it's release_year.\
+Shows with a Rating Y (All Children) also have a negative correlation with it's google score.\
+
+### Discussion
+
+Throughout the process, I noted a few thing that might affect the accuracy of the model.\
+1. All the shows in the data set are selected by Netflix, in no way does it represent all the shows that exist in the world.\
+2.
+Since I only use the data if I can retrieve it’s Google Review Score data, the shows that are in analysed in the model are biased.
+For example, Google will most likely only be able to provide data for well-known shows in the English speaking world.
+Furthermore, show titles which are not unique enough are less likely to have a Google Score  search result.\
+3.
+IMDB Top Actors and Directors Lists are likely to be biased towards the English speaking world, meaning cast or director that could be hugely popular in their origin country might not be classified as “Known”.\
+\
+The random quirks of this sample could cause and overfitting of the multi regression model and reduce its usability on datasets from the non-Netflix world.\
+That being said, the large amount of oversations that we have (6511 titles) could ease the risk of overfitting. \
+\
+There were still a lot of features that could have been created with the dataset. \
+For example, more data from Google could have been scraped, more features could have been engineered from the existing Netflix dataset, etc. \
+However, I took steps to avoid the curse of dimensionality, which indicates that the number of samples needed to estimate an arbitrary function with a given level of accuracy grows exponentially with respect to the number of input variables.\
+From the data I had, I selected features which I found most interesting and likely to explain the score \
+\
+Similarly, I also considered how interpretable the features in the model were.\
+ Although certain features could increase model accuracy, they also increased model complexity, at the cost of interpretability.\
+All the features apart from the LSA value are very easility interpretable features.\
+\
+Another issue I was looking out for was the bias-variance trade off.\
+If our model is too simple and has very few parameters then it may have high bias and low variance.\
+On the other hand if our model has large number of parameters then it’s going to have high variance and low bias\

### 2023-02-18 Packages.r

@@ -11,4 +11,6 @@
 # install.packages("reticulate")
 # install.packages("Hmisc")
 # install.packages("ggcorrplot")
-install.packages("forcats")
+# install.packages("forcats")
+install.packages("jtools")
+

### 2023-02-18 python files/ImageScraping.py

@@ -1,0 +1,57 @@
+
+import pandas as pd
+import requests
+import urllib
+from requests_html import HTML
+from requests_html import HTMLSession
+import bs4
+
+# Defining Functions
+def get_source(url):
+    """Return the source code for the provided URL. 
+    Args: 
+        url (string): URL of the page to scrape.
+    Returns:
+        response (object): HTTP response object from requests_html. 
+    """
+
+    try:
+        session = HTMLSession()
+        response = session.get(url)
+        return response
+
+    except requests.exceptions.RequestException as e:
+        print(e)
+
+def get_googleImage(title):
+
+    scrapedData = []
+
+    query = urllib.parse.quote_plus(title)
+    # response = get_source("https://www.google.co.uk/search?q=" + query)
+    response = get_source("https://en.wikipedia.org/wiki/" + query)
+
+    soup = bs4.BeautifulSoup(response.text,"html.parser")
+                        
+    image_object=soup.find_all( "td", {"class":"infobox-image"} )
+    # print(type(image_object))
+
+    scrapedData.append('Title: ' +title)
+
+    for div in image_object:
+        image = (div.find('img')['src'])
+        print(div.find('img')['src'])
+        scrapedData.append('https:' +image)
+    
+    return scrapedData
+
+# Test Function
+print("hi")
+get_googleImage("Brad_pitt")
+
+
+# Apply data scraping function on all movie/show titles in dataset and save info into new CSV
+data = pd.read_csv('datasets/IMDB image scraping.csv',nrows=20)
+goolgeInfo = data['Wiki_Name'].apply(get_googleImage)
+goolgeInfo.to_csv('wikiInfo.csv', encoding='utf-8', index=False)
+
